---
title: "Conditioned Stimulus rating and Instrumental Conditioning, Cherkasova et al, 2018"
author: "Mariya Cherkasova"
date: "`r Sys.Date()`"
output: html_document
---
Analysis of CS+ and CS- subjective liking ratings and of operant conditioning performance, Cherkasova et al, 2018 study
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Load packages
```{r, packages, include=FALSE}

rm(list=ls()) #clear env
library(lme4)
library(lattice)
library(lmerTest)
library(emmeans)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(influence.ME)
library(gmodels)#CI
library(corrplot)
library(arm)
library(gridExtra)
library(sjPlot)
library(report)
library(BayesFactor)
library(bayestestR)

```
### Ratings data
```{r, include=FALSE}
# # ST1
# st1 <- data.frame(id=0, version=0, CSplus=0, CSminus=0)
# datadir <- "ST_JN_ST/ST1/"
# files <- list.files(path=datadir, pattern="*.*")
# for(i in files){
#   data <- read.delim(paste0(datadir,i,"/RESULTS_FILE.txt"))
#   data <- c(i,1, data[41,5],data[41,6])
#   names(data)=names(st1)
#   st1=rbind(st1,data)
# }
# st1=st1[-1,]
# 
# # ST2
# st2 <- data.frame(id=0, version=0, CSplus=0, CSminus=0)
# datadir <- "ST_JN_ST/ST2/"
# files <- list.files(path=datadir, pattern="*.*")
# for(i in files){
#   data <- read.delim(paste0(datadir,i,"/RESULTS_FILE.txt"))
#   data <- c(i,2, data[41,5],data[41,6])
#   names(data)=names(st2)
#   st2=rbind(st2,data)
# }
# st2=st2[-1,]
# 
# # ST3
# st3 <- data.frame(id=0,version=0, CSplus=0, CSminus=0)
# datadir <- "ST_JN_ST/ST3/"
# files <- list.files(path=datadir, pattern="*.*")
# for(i in files){
#   data <- read.delim(paste0(datadir,i,"/RESULTS_FILE.txt"))
#   data <- c(i,3, data[41,6],data[41,5])
#   names(data)=names(st3)
#   st3=rbind(st3,data)
# }
# st3=st3[-1,]
# 
# # ST4
# st4 <- data.frame(id=0,version=0, CSplus=0, CSminus=0)
# datadir <- "ST_JN_ST/ST4/"
# files <- list.files(path=datadir, pattern="*.*")
# for(i in files){
#   data <- read.delim(paste0(datadir,i,"/RESULTS_FILE.txt"))
#   data <- c(i,4, data[41,6],data[41,5])
#   names(data)=names(st4)
#   st4=rbind(st4,data)
# }
# st4=st4[-1,]
# 
# ratings <- rbind(st1,st2,st3,st4)
# ratings$CSplus <- as.numeric(ratings$CSplus)
# ratings$CSminus <- as.numeric(ratings$CSminus)
# ratings$CSplus_num <- ifelse(ratings$CSplus<351,1,ifelse(ratings$CSplus<487,2,ifelse(ratings$CSplus<614,3,ifelse(ratings$CSplus<729,4,5))))
# ratings$CSminus_num <- ifelse(ratings$CSminus<351,1,ifelse(ratings$CSminus<487,2,ifelse(ratings$CSminus<614,3,ifelse(ratings$CSminus<729,4,5))))
# 
# ratings <- ratings %>% 
#   arrange(id)
# 
# write.csv(ratings, file="ratings_jn.csv", row.names=FALSE)
ratings <- read_csv("ratings_jn.csv")

```

### Combine with sign-tracking

```{r}
STGT <- read.csv("STGT_CSplus2_tertiary_splitJN.csv")
#STGT$id <- as.character(STGT$id)

ratings <- inner_join(ratings,STGT, by="id")
#ratings$STGT <- STGT$STGT
#ratings$gazeidx <- STGT$gazeidx

ratings_long <- ratings %>% 
  pivot_longer(cols=c(CSplus_num,CSminus_num),names_to = "CS")

ratings_long$version <- as.factor(ratings_long$version)


```
### Ratings categorical model
```{r}
ratings_longXim <- ratings_long %>% 
  filter(!STGT_ter=="IM")

ml <- glm(value~ CS*STGT_ter + version, data=ratings_longXim) 
summary(ml)

plot_model(ml ,type="pred", terms=c("CS","STGT_ter"),pred.type="fe", grid = FALSE, colors=c( "orangered","black"))

p <- ratings_longXim %>% 
  ggplot(aes(x=CS, y=value, fill=STGT_ter)) +
  geom_boxplot(alpha=0.6) +
  geom_jitter(aes(colour=STGT,group=STGT_ter), position = position_jitterdodge(), shape=21, size=3, colour="black")+
  xlab("") +
  scale_x_discrete(labels=(c("CS-", "CS+")))+
  scale_colour_manual(values=c("black", "orange")) + 
  scale_fill_manual(values=c("grey","orange")) + 
  theme_bw() +theme(plot.background = element_blank(),panel.grid.major = element_blank(),panel.grid.minor = element_blank()) + 
  theme(panel.border= element_blank(),legend.title = element_blank()) +
  theme(axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5), 
        axis.text.x=element_text(angle=0, size=12, face="bold", vjust=0.5),
        axis.text.y=element_text(angle=0, size=12, vjust=0.5),
        axis.title=element_text(size=14)) + ylab("Subjective liking ratings") 

p
#ggsave(filename="CS_liking_NCRG.tiff", plot=p, width = 6, height = 4.5 )

# Check if removing influential observations makes a diff: it does not

#ratings_longX <- ratings_long[-133,]
#ml.1 <- glm(value~ CS*STGT + version, data=ratings_longX) 
#summary(ml.1)
```

### Ratings dimensional model

```{r}
ml.1 <- glm(value~ gazeidx*CS + version, data=ratings_long) 
summary(ml.1)

plot_model(ml.1 ,type="pred", terms=c("gazeidx","CS"),pred.type="fe", grid = FALSE, colors=c( "orangered","black"))

p <- ratings_long %>% 
  ggplot(aes(x=CS, y=value)) +
  geom_boxplot(alpha=0.6, outlier.shape=8) +
  geom_jitter(width=0.25,height = 0.1)+
  xlab("") +
  scale_x_discrete(labels=(c("CS-", "CS+")))+
  theme_bw() +theme(plot.background = element_blank(),panel.grid.major = element_blank(),panel.grid.minor = element_blank()) + 
  theme(panel.border= element_blank(),legend.title = element_blank()) +
  theme(axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5), 
        axis.text.x=element_text(angle=0, size=12, face="bold", vjust=0.5),
        axis.text.y=element_text(angle=0, size=12, vjust=0.5),
        axis.title=element_text(size=14)) + ylab("Subjective liking ratings") 

p
ggsave(filename="CS_liking_JN.tiff", plot=p, width = 6, height = 4.5 )
```

### Ratings Bayesian categorical model 
```{r}
full <- lmBF(value~ STGT_ter + CS + STGT_ter:CS + version, data=ratings_longXim, iterations = 10000)
describe_posterior(full, test=c("p_direction"))
interaction_null <- lmBF(value~ STGT_ter + CS + version, data=ratings_longXim, iterations = 10000)
gazeidx_null <- lmBF(value~ CS + version, data=ratings_longXim, iterations = 10000)
cs_null <- lmBF(value~ STGT_ter + version, data=ratings_longXim, iterations = 10000)

full/interaction_null
full/gazeidx_null
full/cs_null

# Diagnostics
full_post <- lmBF(value~ STGT_ter + CS + STGT_ter:CS + version, data=ratings_long, iterations = 10000, posterior = TRUE)

#plots
par(mar=c(1,1,1,1))
plot(full_post)

```
### Ratings Bayesian dimensional model

```{r}
full <- lmBF(value~ gazeidx + CS + gazeidx:CS + version, data=ratings_long, iterations = 10000)
describe_posterior(full, test=c("p_direction"))
interaction_null <- lmBF(value~ gazeidx + CS + version, data=ratings_long, iterations = 10000)
gazeidx_null <- lmBF(value~ CS + version, data=ratings_long, iterations = 10000)
cs_null <- lmBF(value~ gazeidx + version, data=ratings_long, iterations = 10000)

full/interaction_null
full/gazeidx_null
full/cs_null

# Diagnostics
full_post <- lmBF(value~ gazeidx + CS + gazeidx:CS + version, data=ratings_long, iterations = 10000, posterior = TRUE)

#plots
par(mar=c(1,1,1,1))
plot(full_post)

```


Check if removing influential observations makes a difference: it does not
```{r}

ratings_longX <- ratings_long[-133,]
ml.2 <- glm(value~ CS*gazeidx + version, data=ratings_longX) 
summary(ml.2)
```

# Operant data

```{r, include=FALSE}
ic <- read.csv("pct_IC.csv")
names(ic)[1]<-"id"
ic$id <- as.character(ic$id)

ic_tertiary <- inner_join(ic, ratings, by="id") %>% 
  rename(STGT=STGT_ter.x)
ic_tertiary$version <- as.factor(ic_tertiary$version)

hist(ic_tertiary$percent_congruent)

```

### Operant conditioning model categorical

```{r}
ml.o <- lm(percent_congruent~ STGT + version, data=filter(ic_tertiary,!STGT=="IM")) 
summary(ml.o)


#plot_model(ml.o, type="pred", terms="STGT",pred.type="fe", grid = FALSE)

p.1 <- ic_tertiary %>% 
  filter(!STGT=="IM") %>% 
  ggplot(aes(x=STGT, y=percent_congruent, fill=STGT)) +
  geom_boxplot(position=position_dodge(width=0.8), alpha=0.6) +
  geom_jitter(aes(colour=STGT), width=0.1, shape=21, size=3, colour="black")+
  xlab("") +
  scale_fill_manual(values=c("grey", "orange")) + 
  theme_bw() +theme(plot.background = element_blank(),panel.grid.major = element_blank(),panel.grid.minor = element_blank()) + 
  theme(panel.border= element_blank(), legend.title = element_blank()) +
  theme(axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5), 
        axis.text.x=element_text(angle=0, size=12, face="bold", vjust=0.5),
        axis.text.y=element_text(angle=0, size=12, vjust=0.5),
        axis.title=element_text(size=14)) + ylab("% Rewarded response") 
p.1
#ggsave(filename="operant_JN.tiff", plot=p.1, width = 6, height = 4.5 )
```
### Operant conditioning model dimensional

```{r}
ml.o1 <- lm(percent_congruent ~ gazeidx + version, data=ic_tertiary) 
summary(ml.o1)

```

### Operant conditioning Bayesian regression categorical

```{r}
#BayesFactor

full <- lmBF(percent_congruent ~ STGT + version, data = filter(ic_tertiary, STGT==c("ST","GT")), iterations = 10000)
describe_posterior(full,test=c("p_direction"))
null <- lmBF(percent_congruent ~ version, data = filter(ic_tertiary, STGT==c("ST","GT")), iterations = 10000)
full/null

# Diagnostics
full_post <- lmBF(percent_congruent~ STGT + version, data = ic_tertiary, iterations = 10000, posterior = TRUE)

#plots
par(mar=c(1,1,1,1))
plot(full_post)

```

### Operant conditioning Bayesian regression dimensional
```{r}
full <- lmBF(percent_congruent ~ gazeidx + version, data = ic_tertiary, iterations = 10000)
describe_posterior(full,test=c("p_direction"))
null <- lmBF(percent_congruent ~ version, data = ic_tertiary, iterations = 10000)
full/null

# Diagnostics
full_post <- lmBF(percent_congruent~ gazeidx + version, data = ic_tertiary, iterations = 10000, posterior = TRUE)

#plots
par(mar=c(1,1,1,1))
plot(full_post)

```


### One sample t-test
```{r}
t.test(ic_tertiary$percent_congruent, mu = 50.0, alternative = "greater")

#write.csv(ic_tertiary, "ic_tertiaryJN.csv")
```

### Bayesian one sample t-test

```{r}

H0_mean <- 50  

# Perform Bayesian one-sample t-test
result <- ttestBF(ic_tertiary$percent_congruent, mu = H0_mean)

# Summary of the Bayesian t-test
print(result)

```

# Regression diagnostics

```{r}
plot(ml)
# Cook's D plot
# identify D values > 4/(n-k-1)
cutoff <- 4/(nrow(ratings_longXim)-length(ml$coefficients)-1)
plot(ml, which=4)

plot(ml.1)
# Cook's D plot
# identify D values > 4/(n-k-1)
cutoff <- 4/(nrow(ratings_long)-length(ml.1$coefficients)-1)
plot(ml.1, which=4)

plot(ml.o)
# Cook's D plot
# identify D values > 4/(n-k-1)
cutoff <- 4/(nrow(ic_tertiary)-length(ml.o$coefficients)-1)
plot(ml.o, which=4)

plot(ml.o1)
# Cook's D plot
# identify D values > 4/(n-k-1)
cutoff <- 4/(nrow(ic_tertiary)-length(ml.o1$coefficients)-1)
plot(ml.o1, which=4)

```


