---
title: "Conditioned Stimulus rating and Instrumental Conditioning, Study 2"
author: "Mariya Cherkasova"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---
Analysis of CS+ and CS- subjective liking ratings, reward likelihood ratings, and of operant conditioning performance, Study 2
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Libraries
```{r, packages, include=FALSE}

rm(list=ls()) #clear env
library(lme4)
library(lattice)
library(lmerTest)
library(emmeans)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(influence.ME)
library(gmodels)#CI
library(corrplot)
library(arm)
library(gridExtra)
library(sjPlot)
library(BayesFactor)
library(bayestestR)
library(report)

```
Read in data
```{r, include=FALSE}
ratings <- read.csv("rating_IC_NCRG.csv")
names(ratings)[1] <- "id"
stdata <- read.csv("STGT_CSplus2_tertiary_split_NCRG.csv")

# Trim the data
a <- ratings$id
b <- stdata$id
to_ex <- setdiff(a,b)

df <- ratings %>% 
  filter(!id %in% to_ex)
df$gazeidx <- stdata$gazeidx
df$STGT <- stdata$STGT_ter
df$version_p <- ifelse(df$version==1|df$version==2,1,2)
df$version_p <- factor(df$version_p)
df$version_o <- ifelse(df$version==1|df$version==3,1,2)
df$version_o <- factor(df$version_o)

# Pivot long
df_l_a <- df %>% 
  pivot_longer(cols = c(CSplusAware,CSminusAware),names_to = "CS")

df_l_r <- df %>% 
  pivot_longer(cols = c(Csplus_rating,Csminus_rating),names_to = "CS")

# Exclude intermediates
df_l_a_ter <- df_l_a %>% 
  filter(!STGT=="IM")

df_l_r_ter <- df_l_r %>% 
  filter(!STGT=="IM")

```
### Liking ratings categorical model
```{r}
ml <- glm(value ~ CS*STGT + version_p, data=df_l_r_ter) 
summary(ml)

plot_model(ml ,type="pred", terms=c("CS","STGT"),pred.type="fe", grid = FALSE, colors=c( "orangered","black"))

p.1 <- df_l_r_ter %>% 
  ggplot(aes(x=CS, y=value, colour=STGT, fill=STGT))+
  geom_boxplot(alpha=0.6) +
  geom_jitter(aes(colour=STGT,group=STGT), position = position_jitterdodge(), shape=21, size=3, colour="black")+
  xlab("") +
  scale_x_discrete(labels=(c("CS-", "CS+")))+
  scale_colour_manual(values=c("black", "orange")) + 
  scale_fill_manual(values=c("grey", "orange")) + 
  theme_bw() +theme(plot.background = element_blank(),panel.grid.major = element_blank(),panel.grid.minor = element_blank(),legend.title = element_blank()) + 
  theme(panel.border= element_blank()) +
  theme(axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5), 
        axis.text.x=element_text(angle=0, size=12, face="bold", vjust=0.5),
        axis.text.y=element_text(angle=0, size=12, vjust=0.5),
        axis.title=element_text(size=14)) + ylab("Subjective liking ratings") 
p.1
#ggsave(filename="ratings_NCRG.tiff", plot=p.1, width = 6, height = 4.5 )
```
### Liking ratings categorical model (Bayesian)

```{r}
full <- lmBF(value~ STGT + CS + STGT:CS + version, data=df_l_r_ter, iterations = 10000)
describe_posterior(full,test=c("p_direction"))
interaction_null <- lmBF(value~ STGT + CS + version, data=df_l_r_ter, iterations = 10000)
STGT_null <- lmBF(value~ CS + version, data=df_l_r_ter, iterations = 10000)
cs_null <- lmBF(value~ STGT + version, data=df_l_r_ter, iterations = 10000)

full/interaction_null
full/STGT_null
full/cs_null

# Diagnostics
full_post <- lmBF(value~ STGT + CS + STGT:CS + version, data=df_l_r_ter, iterations = 10000, posterior = TRUE)

#plots
par(mar=c(1,1,1,1))
plot(full_post)

```
### Ratings model dimensional
```{r}
ml.2 <- glm(value ~ CS*gazeidx + version, data=df_l_r) 
summary(ml.2)

plot_model(ml.2 ,type="pred", terms=c("gazeidx","CS"),pred.type="fe", grid = FALSE)

p.2 <- df_l_r %>% 
  ggplot(aes(x=CS, y=value))+
  geom_boxplot(alpha=0.6) +
  geom_jitter(width=0.25,height = 0.1)+
  xlab("") +
  scale_x_discrete(labels=(c("CS-", "CS+")))+
  #scale_colour_manual(values=c("black", "orange")) + 
  #scale_fill_manual(values=c("grey", "orange")) + 
  theme_bw() +theme(plot.background = element_blank(),panel.grid.major = element_blank(),panel.grid.minor = element_blank(),legend.title = element_blank()) + 
  theme(panel.border= element_blank()) +
  theme(axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5), 
        axis.text.x=element_text(angle=0, size=20, face="bold", vjust=0.5),
        axis.text.y=element_text(angle=0, size=20, vjust=0.5),
        axis.title=element_text(size=20)) + ylab("Subjective liking ratings") 
p.2

ggsave(filename="CS_liking_NCRG1.tiff", plot=p.2, width = 6, height = 4.5 )
```

### Ratings model dimensional(Bayesian)
```{r}
full <- lmBF(value~ gazeidx + CS + gazeidx:CS + version, data=df_l_r, iterations = 10000)
describe_posterior(full,test=c("p_direction"))
interaction_null <- lmBF(value~ gazeidx + CS + version, data=df_l_r, iterations = 10000)
gazeidx_null <- lmBF(value~ CS + version, data=df_l_r, iterations = 10000)
cs_null <- lmBF(value~ gazeidx + version, data=df_l_r, iterations = 10000)

full/interaction_null
full/gazeidx_null
full/cs_null

# Diagnostics
full_post <- lmBF(value~ gazeidx + CS + gazeidx:CS + version, data=df_l_r, iterations = 10000, posterior = TRUE)

#plots
par(mar=c(1,1,1,1))
plot(full_post)

```
### Awareness rating categorical model

```{r}
ml.3 <- glm(value ~ CS*STGT + version_p, data=df_l_a_ter) 
summary(ml.3)

plot_model(ml.3 ,type="pred", terms=c("STGT"),pred.type="fe", grid = FALSE)

p.3 <- df_l_a_ter %>% 
  ggplot(aes(x=CS, y=value, colour=STGT, fill=STGT)) +
  geom_boxplot(alpha=0.6) +
  geom_jitter(aes(colour=STGT,group=STGT), position = position_jitterdodge(), shape=21, size=3, colour="black")+
  xlab("") +
  scale_x_discrete(labels=(c("CS-", "CS+")))+
  scale_colour_manual(values=c("black", "orange")) + 
  scale_fill_manual(values=c("grey", "orange")) + 
  theme_bw() +theme(plot.background = element_blank(),panel.grid.major = element_blank(),panel.grid.minor = element_blank(), legend.title = element_blank()) + 
  theme(panel.border= element_blank()) +
  theme(axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5), 
        axis.text.x=element_text(angle=0, size=12, face="bold", vjust=0.5),
        axis.text.y=element_text(angle=0, size=12, vjust=0.5),
        axis.title=element_text(size=14)) + ylab("Reward likelihood rating") 
p.3
#ggsave(filename="awareness_NCRG.tiff", plot=p.3, width = 6, height = 4.5 )
```
### Awareness rating categorical model(Bayesian)

```{r}
full <- lmBF(value~ STGT + CS + STGT:CS + version, data=df_l_a_ter, iterations = 10000)
describe_posterior(full,test=c("p_direction"))
interaction_null <- lmBF(value~ STGT + CS + version, data=df_l_a_ter, iterations = 10000)
STGT_null <- lmBF(value~ CS + version, data=df_l_a_ter, iterations = 10000)
cs_null <- lmBF(value~ STGT + version, data=df_l_a_ter, iterations = 10000)

full/interaction_null
full/STGT_null
full/cs_null

# Diagnostics
full_post <- lmBF(value~ STGT + CS + STGT:CS + version, data=df_l_a_ter, iterations = 10000, posterior = TRUE)

#plots
par(mar=c(1,1,1,1))
plot(full_post)

```
Check if influential observations change results:
```{r}
# 43 changes the trend for STGT to significance, but no real reason to remove observation
# 36 no change
# 45 no change
# df_l_a_terX <- df_l_a_ter[-45,]
# ml.3X <- glm(value ~ CS*STGT + version, data=df_l_a_terX) 
# summary(ml.3X)
```


### Awareness rating dimensional model
```{r}
ml.4 <- glm(value ~ CS*gazeidx + version_p, data=df_l_a) 
summary(ml.4)

plot_model(ml.4 ,type="pred", terms=c("gazeidx"),pred.type="fe", grid = FALSE)

p.4 <- df_l_a %>% 
  ggplot(aes(x=CS, y=value)) +
  geom_boxplot(alpha=0.6, outlier.shape=8) +
  geom_jitter()+
  xlab("") +
  scale_x_discrete(labels=(c("CS-", "CS+")))+
  #scale_colour_manual(values=c("black", "orange")) + 
  #scale_fill_manual(values=c("grey", "orange")) + 
  theme_bw() +theme(plot.background = element_blank(),panel.grid.major = element_blank(),panel.grid.minor = element_blank(), legend.title = element_blank()) + 
  theme(panel.border= element_blank()) +
  theme(axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5), 
        axis.text.x=element_text(angle=0, size=20, face="bold", vjust=0.5),
        axis.text.y=element_text(angle=0, size=20, vjust=0.5),
        axis.title=element_text(size=20)) + ylab("Reward likelihood rating") 
p.4

ggsave(filename="CS_awareness_NCRG1.tiff", plot=p.4, width = 6, height = 4.5 )
```


### Ratings model dimensional (Bayesian)

```{r}

full <- lmBF(value~ gazeidx + CS + gazeidx:CS + version, data=df_l_a, iterations = 10000)
describe_posterior(full,test=c("p_direction"))
interaction_null <- lmBF(value~ gazeidx + CS + version, data=df_l_a, iterations = 10000)
gazeidx_null <- lmBF(value~ CS + version, data=df_l_a, iterations = 10000)
cs_null <- lmBF(value~ gazeidx + version, data=df_l_a, iterations = 10000)

full/interaction_null
full/gazeidx_null
full/cs_null

# Diagnostics
full_post <- lmBF(value~ gazeidx + CS + gazeidx:CS + version, data=df_l_a, iterations = 10000, posterior = TRUE)

#plots
par(mar=c(1,1,1,1))
plot(full_post)

```

# Operant conditioning 
### Cattegorical model
```{r}
df_ic_ter <- df %>% 
  filter(!STGT=="IM")
df_ic_ter$IC_dec <- df_ic_ter$IC/100

ml.5 <- glm(IC ~ STGT + version_o, data=df_ic_ter) 
summary(ml.5)

p.5 <- df_ic_ter %>% 
  ggplot(aes(x=STGT, y=IC, fill=STGT)) +
  geom_boxplot(position=position_dodge(width=0.8), alpha=0.6) +
  geom_jitter(aes(colour=STGT), width=0.1, shape=21, size=3, colour="black")+
  xlab("") +
  scale_fill_manual(values=c("azure4", "orange")) + 
  theme_bw() +theme(plot.background = element_blank(),panel.grid.major = element_blank(),panel.grid.minor = element_blank()) + 
  theme(panel.border= element_blank()) +
  theme(axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5), 
        axis.text.x=element_text(angle=0, size=12, face="bold", vjust=0.5),
        axis.text.y=element_text(angle=0, size=12, vjust=0.5),
        axis.title=element_text(size=14)) + ylab("% Rewarded response") 
p.5
#ggsave(filename="operant_NCRG.tiff", plot=p.3, width = 6, height = 4.5 )
```

### Operant conditioning model categorical (Bayesian)

```{r}
full <- lmBF(IC ~ STGT + version_o, data = df_ic_ter, iterations = 10000)
describe_posterior(full,test=c("p_direction"))
null <- lmBF(IC ~ version_o, data = df_ic_ter, iterations = 10000)
full/null

# Diagnostics
full_post <- lmBF(IC ~ STGT + version_o, data = df_ic_ter, iterations = 10000, posterior = TRUE)

#plots
par(mar=c(1,1,1,1))
plot(full_post)
```

### Operant conditioning model dimensional

```{r}

ml.6 <- glm(IC ~ gazeidx + version_o, data=df_ic_ter) 
summary(ml.6)

```
### One sample t-test
```{r}
t.test(df$IC, mu = 50.0, alternative = "greater")
```
### Operant conditioning model dimensional (Bayesian)

```{r}
full <- lmBF(IC ~ gazeidx + version_o, data = df, iterations = 10000)
describe_posterior(full,test=c("p_direction"))
null <- lmBF(IC ~ version, data = df, iterations = 10000)
full/null

# Diagnostics
full_post <- lmBF(IC ~ gazeidx + version, data = df, iterations = 10000, posterior = TRUE)

#plots
par(mar=c(1,1,1,1))
plot(full_post)

```
### One sample t-test Bayesian

```{r}
# Specify the null hypothesis mean (H0) and the alternative hypothesis mean (H1)
H0_mean <- 50  # Null hypothesis mean
#H1_mean <- 5.8  # Alternative hypothesis mean

# Perform Bayesian one-sample t-test
result <- ttestBF(df$IC, mu = H0_mean)

# Summary of the Bayesian t-test
print(result)

```

### Regression diagnostics

```{r}
plot(ml)
# Cook's D plot
# identify D values > 4/(n-k-1)
cutoff <- 4/(36-length(ml$coefficients)-1)
plot(ml, which=4)

plot(ml.2)
# Cook's D plot
# identify D values > 4/(n-k-1)
cutoff <- 4/(36-length(ml.2$coefficients)-1)
plot(ml.2, which=4)

plot(ml.3)
# Cook's D plot
# identify D values > 4/(n-k-1)
cutoff <- 4/(36-length(ml.3$coefficients)-1)
plot(ml.3, which=4)

plot(ml.4)
# Cook's D plot
# identify D values > 4/(n-k-1)
cutoff <- 4/(36-length(ml.4$coefficients)-1)
plot(ml.4, which=4)

plot(ml.5)
# Cook's D plot
# identify D values > 4/(n-k-1)
cutoff <- 4/(36-length(ml.5$coefficients)-1)
plot(ml.5, which=4)

plot(ml.6)
# Cook's D plot
# identify D values > 4/(n-k-1)
cutoff <- 4/(36-length(ml.6$coefficients)-1)
plot(ml.6, which=4)
```
