---
title: "Pavlovian to Instrumental Transfer, Cherkasova et al, 2018"
author: "Mariya Cherkasova"
date: "`r Sys.Date()`"
output: html_document
---
PIT analysis: Cherkasova et al, 2018 dataset
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Load packages, read in the data
```{r, packages, include=FALSE}

rm(list=ls()) #clear env
library(lme4)
library(lattice)
library(lmerTest)
library(emmeans)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(influence.ME)
library(gmodels)#CI
library(corrplot)
library(arm)
library(gridExtra)
library(sjPlot)
library(olsrr)
library(BayesFactor)
library(bayestestR)

```
# PIT1
-Congruent response -left; incongruent response - right; CS+=win_fractal=blue (no re-labeling)
PIT=(number of congruent-incongruent choices/total number of choices)
```{r, include=FALSE}
# pit1data <- data.frame(id=0, trial=0, fractal=0,stimulus=0, click_location=0,decision_RT=0)
# 
# datadir <- "ST_JN_PIT/PIT1/results/"
# files <- list.files(path=datadir, pattern="*.*")
# for(i in files){
#   data <- read.delim(paste0(datadir,i,"/RESULTS_FILE.txt"))
#   id <- rep(i,nrow(data))
#   data <- cbind(id,data)
#   names(data)=names(pit1data)
#   pit1data=rbind(pit1data,data)
# }
# pit1data=pit1data[-1,]
# 
# pit1data$response <- ifelse(pit1data$click_location<500,"congruent","incongruent")
# pit1data$half <- ifelse(pit1data$trial<=7,1,2) # half
# pit1data$block <- ifelse(pit1data$trial<=5,1,ifelse(pit1data$trial<=9,2,3)) #block
# 
# # not considering task half
# pit1 <- pit1data %>% 
#   group_by(id,stimulus,response) %>% 
#   summarise(n=n()) %>% 
#   pivot_wider(names_from = response, values_from=n)
# 
# pit1$incongruent <- replace_na(pit1$incongruent,0) # Replace NAs
# pit1$congruent <- replace_na(pit1$congruent,0)
# pit1$response_idx <- (pit1$congruent-pit1$incongruent)/(pit1$congruent+pit1$incongruent)
# pit1$version <- rep(1,nrow(pit1))
# 
# # considering task half
# pit1_h <- pit1data %>% 
#   group_by(id,stimulus,response,half) %>% 
#   summarise(n=n()) %>% 
#   pivot_wider(names_from = c(response,half), values_from=n)
# 
# pit1_h$incongruent_1 <- replace_na(pit1_h$incongruent_1,0) # Replace NAs
# pit1_h$congruent_1 <- replace_na(pit1_h$congruent_1,0)
# pit1_h$incongruent_2 <- replace_na(pit1_h$incongruent_2,0)
# pit1_h$congruent_2 <- replace_na(pit1_h$congruent_2,0)
# pit1_h$response_idxh1 <- (pit1_h$congruent_1-pit1_h$incongruent_1)/(pit1_h$congruent_1+pit1_h$incongruent_1)
# pit1_h$response_idxh2 <- (pit1_h$congruent_2-pit1_h$incongruent_2)/(pit1_h$congruent_2+pit1_h$incongruent_2)
# pit1_h$version <- rep(1,nrow(pit1_h))
# 
# # considering task block
# pit1_b <- pit1data %>% 
#   group_by(id,stimulus,response,block) %>% 
#   summarise(n=n()) %>% 
#   pivot_wider(names_from = c(response,block), values_from=n)
# 
# pit1_b$incongruent_1 <- replace_na(pit1_b$incongruent_1,0) # Replace NAs
# pit1_b$congruent_1 <- replace_na(pit1_b$congruent_1,0)
# pit1_b$incongruent_2 <- replace_na(pit1_b$incongruent_2,0)
# pit1_b$congruent_2 <- replace_na(pit1_b$congruent_2,0)
# pit1_b$incongruent_3 <- replace_na(pit1_b$incongruent_3,0)
# pit1_b$congruent_3 <- replace_na(pit1_b$congruent_3,0)
# pit1_b$version <- rep(1,nrow(pit1_b))
# 
# pit1_b <- pit1_b %>% 
#   filter(!stimulus=="filler")
# 
# pit1_b$response_idxh1 <- (pit1_b$congruent_1-pit1_b$incongruent_1)/(pit1_b$congruent_1+pit1_b$incongruent_1)
# pit1_b$response_idxh2 <- (pit1_b$congruent_2-pit1_b$incongruent_2)/(pit1_b$congruent_2+pit1_b$incongruent_2)
# pit1_b$response_idxh3 <- (pit1_b$congruent_3-pit1_b$incongruent_3)/(pit1_b$congruent_3+pit1_b$incongruent_3)

```
# PIT2
-Congruent response -right; incongruent response - left; CS+=win_fractal=blue (no re-labeling)
```{r, include=FALSE}
# 
# pit2data <- data.frame(id=0, trial=0, fractal=0,stimulus=0, click_location=0,decision_RT=0)
# 
# datadir <- "ST_JN_PIT/PIT2/results/"
# files <- list.files(path=datadir, pattern="*.*")
# for(i in files){
#   data <- read.delim(paste0(datadir,i,"/RESULTS_FILE.txt"))
#   id <- rep(i,nrow(data))
#   data <- cbind(id,data)
#   names(data)=names(pit2data)
#   pit2data=rbind(pit2data,data)
# }
# pit2data=pit2data[-1,]
# 
# pit2data$response <- ifelse(pit2data$click_location<500,"incongruent","congruent")
# pit2data$half <- ifelse(pit2data$trial<=7,1,2) #half
# pit2data$block <- ifelse(pit2data$trial<=5,1,ifelse(pit2data$trial<=9,2,3)) #block
# 
# # not considering task half
# pit2 <- pit2data %>% 
#   group_by(id,stimulus,response) %>% 
#   summarise(n=n()) %>% 
#   pivot_wider(names_from = response, values_from=n)
# 
# pit2$incongruent <- replace_na(pit2$incongruent,0) # Replace NAs
# pit2$congruent <- replace_na(pit2$congruent,0)
# pit2$response_idx <- (pit2$congruent-pit2$incongruent)/(pit2$congruent+pit2$incongruent)
# pit2$version <- rep(2,nrow(pit2))
# 
# # considering task half
# pit2_h <- pit2data %>% 
#   group_by(id,stimulus,response,half) %>% 
#   summarise(n=n()) %>% 
#   pivot_wider(names_from = c(response,half), values_from=n)
# 
# pit2_h$incongruent_1 <- replace_na(pit2_h$incongruent_1,0) # Replace NAs
# pit2_h$congruent_1 <- replace_na(pit2_h$congruent_1,0)
# pit2_h$incongruent_2 <- replace_na(pit2_h$incongruent_2,0)
# pit2_h$congruent_2 <- replace_na(pit2_h$congruent_2,0)
# pit2_h$response_idxh1 <- (pit2_h$congruent_1-pit2_h$incongruent_1)/(pit2_h$congruent_1+pit2_h$incongruent_1)
# pit2_h$response_idxh2 <- (pit2_h$congruent_2-pit2_h$incongruent_2)/(pit2_h$congruent_2+pit2_h$incongruent_2)
# pit2_h$version <- rep(2,nrow(pit2_h))
# 
# # considering task block
# pit2_b <- pit2data %>% 
#   group_by(id,stimulus,response,block) %>% 
#   summarise(n=n()) %>% 
#   pivot_wider(names_from = c(response,block), values_from=n)
# 
# pit2_b$incongruent_1 <- replace_na(pit2_b$incongruent_1,0) # Replace NAs
# pit2_b$congruent_1 <- replace_na(pit2_b$congruent_1,0)
# pit2_b$incongruent_2 <- replace_na(pit2_b$incongruent_2,0)
# pit2_b$congruent_2 <- replace_na(pit2_b$congruent_2,0)
# pit2_b$incongruent_3 <- replace_na(pit2_b$incongruent_3,0)
# pit2_b$congruent_3 <- replace_na(pit2_b$congruent_3,0)
# pit2_b$version <- rep(2,nrow(pit2_b))
# 
# pit2_b <- pit2_b %>% 
#   filter(!stimulus=="filler")
# 
# pit2_b$response_idxh1 <- (pit2_b$congruent_1-pit2_b$incongruent_1)/(pit2_b$congruent_1+pit2_b$incongruent_1)
# pit2_b$response_idxh2 <- (pit2_b$congruent_2-pit2_b$incongruent_2)/(pit2_b$congruent_2+pit2_b$incongruent_2)
# pit2_b$response_idxh3 <- (pit2_b$congruent_3-pit2_b$incongruent_3)/(pit2_b$congruent_3+pit2_b$incongruent_3)

```
# PIT3
-Congruent response -left; incongruent response -right; CS+=nowin_fractal=blue (re-labeling)
```{r, include=FALSE}
# pit3data <- data.frame(id=0, trial=0, fractal=0,stimulus=0, click_location=0,decision_RT=0)
# 
# datadir <- "ST_JN_PIT/PIT3/results/"
# files <- list.files(path=datadir, pattern="*.*")
# for(i in files){
#   data <- read.delim(paste0(datadir,i,"/RESULTS_FILE.txt"))
#   id <- rep(i,nrow(data))
#   data <- cbind(id,data)
#   names(data)=names(pit3data)
#   pit3data=rbind(pit3data,data)
# }
# pit3data=pit3data[-1,]
# 
# pit3data$response <- ifelse(pit3data$click_location<500,"congruent","incongruent")
# pit3data$half <- ifelse(pit3data$trial<=7,1,2) # half
# pit3data$block <- ifelse(pit3data$trial<=5,1,ifelse(pit3data$trial<=9,2,3)) #block
# 
# pit3data$stimulus <- ifelse(pit3data$stimulus=="win","nowin",ifelse(pit3data$stimulus=="nowin","win","filler"))
# 
# # not considering task half
# pit3 <- pit3data %>% 
#   group_by(id,stimulus,response) %>% 
#   summarise(n=n()) %>% 
#   pivot_wider(names_from = response, values_from=n)
# 
# pit3$incongruent <- replace_na(pit3$incongruent,0) # Replace NAs
# pit3$congruent <- replace_na(pit3$congruent,0)
# pit3$response_idx <- (pit3$congruent-pit3$incongruent)/(pit3$congruent+pit3$incongruent)
# pit3$version <- rep(3,nrow(pit3))
# 
# # considering task half
# pit3_h <- pit3data %>% 
#   group_by(id,stimulus,response,half) %>% 
#   summarise(n=n()) %>% 
#   pivot_wider(names_from = c(response,half), values_from=n)
# 
# pit3_h$incongruent_1 <- replace_na(pit3_h$incongruent_1,0) # Replace NAs
# pit3_h$congruent_1 <- replace_na(pit3_h$congruent_1,0)
# pit3_h$incongruent_2 <- replace_na(pit3_h$incongruent_2,0)
# pit3_h$congruent_2 <- replace_na(pit3_h$congruent_2,0)
# pit3_h$response_idxh1 <- (pit3_h$congruent_1-pit3_h$incongruent_1)/(pit3_h$congruent_1+pit3_h$incongruent_1)
# pit3_h$response_idxh2 <- (pit3_h$congruent_2-pit3_h$incongruent_2)/(pit3_h$congruent_2+pit3_h$incongruent_2)
# pit3_h$version <- rep(3,nrow(pit3_h))
# 
# # considering task block
# pit3_b <- pit3data %>% 
#   group_by(id,stimulus,response,block) %>% 
#   summarise(n=n()) %>% 
#   pivot_wider(names_from = c(response,block), values_from=n)
# 
# pit3_b$incongruent_1 <- replace_na(pit3_b$incongruent_1,0) # Replace NAs
# pit3_b$congruent_1 <- replace_na(pit3_b$congruent_1,0)
# pit3_b$incongruent_2 <- replace_na(pit3_b$incongruent_2,0)
# pit3_b$congruent_2 <- replace_na(pit3_b$congruent_2,0)
# pit3_b$incongruent_3 <- replace_na(pit3_b$incongruent_3,0)
# pit3_b$congruent_3 <- replace_na(pit3_b$congruent_3,0)
# pit3_b$version <- rep(3,nrow(pit3_b))
# 
# pit3_b <- pit3_b %>% 
#   filter(!stimulus=="filler")
# 
# pit3_b$response_idxh1 <- (pit3_b$congruent_1-pit3_b$incongruent_1)/(pit3_b$congruent_1+pit3_b$incongruent_1)
# pit3_b$response_idxh2 <- (pit3_b$congruent_2-pit3_b$incongruent_2)/(pit3_b$congruent_2+pit3_b$incongruent_2)
# pit3_b$response_idxh3 <- (pit3_b$congruent_3-pit3_b$incongruent_3)/(pit3_b$congruent_3+pit3_b$incongruent_3)
```
# PIT4
-Congruent response -right; incongruent response - left; CS+=nowin_fractal=blue (re-labeling)
```{r, include=FALSE}
# pit4data <- data.frame(id=0, trial=0, fractal=0,stimulus=0, click_location=0,decision_RT=0)
# 
# datadir <- "ST_JN_PIT/PIT4/results/"
# files <- list.files(path=datadir, pattern="*.*")
# for(i in files){
#   data <- read.delim(paste0(datadir,i,"/RESULTS_FILE.txt"))
#   id <- rep(i,nrow(data))
#   data <- cbind(id,data)
#   names(data)=names(pit4data)
#   pit4data=rbind(pit4data,data)
# }
# pit4data=pit4data[-1,]
# 
# pit4data$response <- ifelse(pit4data$click_location<500,"incongruent","congruent") 
# pit4data$half <- ifelse(pit4data$trial<=7,1,2) # half
# pit4data$block <- ifelse(pit4data$trial<=5,1,ifelse(pit4data$trial<=9,2,3)) #block
# pit4data$stimulus <- ifelse(pit4data$stimulus=="win","nowin",ifelse(pit4data$stimulus=="nowin","win","filler"))
# 
# # not considering task half
# pit4 <- pit4data %>% 
#   group_by(id,stimulus,response) %>% 
#   summarise(n=n()) %>% 
#   pivot_wider(names_from = response, values_from=n)
# 
# pit4$incongruent <- replace_na(pit4$incongruent,0) # Replace NAs
# pit4$congruent <- replace_na(pit4$congruent,0)
# pit4$response_idx <- (pit4$congruent-pit4$incongruent)/(pit4$congruent+pit4$incongruent)
# pit4$version <- rep(4,nrow(pit4))
# 
# # considering task half
# pit4_h <- pit4data %>% 
#   group_by(id,stimulus,response,half) %>% 
#   summarise(n=n()) %>% 
#   pivot_wider(names_from = c(response,half), values_from=n)
# 
# pit4_h$incongruent_1 <- replace_na(pit4_h$incongruent_1,0) # Replace NAs
# pit4_h$congruent_1 <- replace_na(pit4_h$congruent_1,0)
# pit4_h$incongruent_2 <- replace_na(pit4_h$incongruent_2,0)
# pit4_h$congruent_2 <- replace_na(pit4_h$congruent_2,0)
# pit4_h$response_idxh1 <- (pit4_h$congruent_1-pit4_h$incongruent_1)/(pit4_h$congruent_1+pit4_h$incongruent_1)
# pit4_h$response_idxh2 <- (pit4_h$congruent_2-pit4_h$incongruent_2)/(pit4_h$congruent_2+pit4_h$incongruent_2)
# pit4_h$version <- rep(4,nrow(pit4_h))
# 
# # considering task block
# pit4_b <- pit4data %>% 
#   group_by(id,stimulus,response,block) %>% 
#   summarise(n=n()) %>% 
#   pivot_wider(names_from = c(response,block), values_from=n)
# 
# pit4_b$incongruent_1 <- replace_na(pit4_b$incongruent_1,0) # Replace NAs
# pit4_b$congruent_1 <- replace_na(pit4_b$congruent_1,0)
# pit4_b$incongruent_2 <- replace_na(pit4_b$incongruent_2,0)
# pit4_b$congruent_2 <- replace_na(pit4_b$congruent_2,0)
# pit4_b$incongruent_3 <- replace_na(pit4_b$incongruent_3,0)
# pit4_b$congruent_3 <- replace_na(pit4_b$congruent_3,0)
# pit4_b$version <- rep(4,nrow(pit4_b))
# 
# pit4_b <- pit4_b %>% 
#   filter(!stimulus=="filler")
# 
# pit4_b$response_idxh1 <- (pit4_b$congruent_1-pit4_b$incongruent_1)/(pit4_b$congruent_1+pit4_b$incongruent_1)
# pit4_b$response_idxh2 <- (pit4_b$congruent_2-pit4_b$incongruent_2)/(pit4_b$congruent_2+pit4_b$incongruent_2)
# pit4_b$response_idxh3 <- (pit4_b$congruent_3-pit4_b$incongruent_3)/(pit4_b$congruent_3+pit4_b$incongruent_3)
# 
# PIT <- rbind(pit1,pit2,pit3,pit4)
# write.csv(PIT, file="pit_jn.csv",row.names=FALSE)
```

# Combine PIT with gaze index

```{r, include=FALSE}
PIT <- read.csv("pit_jn.csv")
PIT <- PIT %>% 
  arrange(id,stimulus) #%>% 

PIT_h <- rbind(pit1_h,pit2_h, pit3_h, pit4_h)
PIT_h <- PIT_h %>% 
  arrange(id,stimulus) #%>% 

stdata <- read.csv("STGT_CSplus2_tertiary_splitJN.csv")
a <- PIT$id
b <- stdata$id
to_ex <- setdiff(a,b)

stdata <- stdata %>% 
  arrange(id)

PIT_conservative <- PIT %>% 
  filter(!id %in% to_ex)

PIT_h_conservative <- PIT_h %>% 
  filter(!id %in% to_ex)

three <- 1:3 # because there are three stimuli 
stexpandIDX <- expand.grid(three,stdata$gazeidx)
stexpandSTGT <- expand.grid(three,stdata$STGT_ter)

PIT_conservative$gazeIDX <- stexpandIDX$Var2
PIT_conservative$STGT <- stexpandSTGT$Var2
PIT_h_conservative$gazeIDX <- stexpandIDX$Var2
PIT_h_conservative$STGT <- stexpandSTGT$Var2

PIT_conservative$stimulus <- factor(PIT_conservative$stimulus, levels = c("win", "nowin", "filler"))
PIT_h_conservative$stimulus <- factor(PIT_h_conservative$stimulus, levels = c("win", "nowin", "filler"))

#view PIT response idx distribution
par(mfrow=c(1,3))
hist(PIT$response_idx)
hist(PIT_h$response_idxh1)
hist(PIT_h$response_idxh2)

```

# Combine with IC data, trim data such that in only includes participants who performed the operant task above chance

```{r, include=FALSE}

ic <- read.csv("pct_IC_meanreplace.csv")
names(ic)[1]<-"id"
icid <- ic$id
PITid <- unique(PIT_conservative$id)

three <- 1:3 # because there are three stimuli 
xpand_ic <- expand.grid(three,ic$percent_congruent)

PIT_conservative$ic <- xpand_ic$Var2
PIT_h_conservative$ic <- xpand_ic$Var2

PIT_conservative_tr <- PIT_conservative %>% 
  filter(ic>53.9)

PIT_h_conservative_tr <- PIT_h_conservative %>% 
  filter(ic>53.9)

```
# ST/GT PIT models
## Models not considering half
### Categorical model
Excluding participants not looking at the CS or US, tertiary split
```{r}
# Tertiary split analysis
PIT_conservative_ter <- PIT_conservative_tr %>% 
  filter(!STGT=="IM")
PIT_conservative_ter$version <- as.factor(PIT_conservative_ter$version)

ml.1 = lm(response_idx ~ STGT*stimulus + version, data=PIT_conservative_ter) 
summary(ml.1)

# Plot 
plot_model(ml.1,type="pred", terms=c("stimulus", "STGT"),pred.type="fe", grid = FALSE, colors=c("orangered","black"))
#plot_model(ml.1a,type="pred", terms=c("stimulus"),pred.type="fe", grid = FALSE)

# checking if excluding 184 makes a diff: makes the trends significnat, but no clear reason to remove participant
#PIT_conservative_terX <- PIT_conservative_ter[-184,] 
#ml.1x = lm(response_idx ~ STGT*stimulus + version, data=PIT_conservative_terX) 
#summary(ml.1x)
```

### Bayesian categorical model
BayesFactor

```{r}
full <- lmBF(response_idx ~ STGT + stimulus + STGT:stimulus + version, data=PIT_conservative_ter, iterations = 10000)
describe_posterior(full, test=c("p_direction"))
interaction_null <- lmBF(response_idx ~ STGT + stimulus + version, data=PIT_conservative_ter, iterations = 10000)
describe_posterior(interaction_null, test=c("p_direction"))
stgt_null <- lmBF(response_idx ~ stimulus + version, data=PIT_conservative_ter, iterations = 10000)
describe_posterior(stgt_null, test=c("p_direction"))
stimulus_null <- lmBF(response_idx ~ STGT + version, data=PIT_conservative_ter, iterations = 10000)
describe_posterior(stimulus_null, test=c("p_direction"))

full/interaction_null
full/stgt_null
full/stimulus_null

# Diagnostics
full_post <- lmBF(response_idx ~ STGT + stimulus + STGT:stimulus + version, data=PIT_conservative_ter, iterations = 10000, posterior = TRUE)

#plots
par(mar=c(1,1,1,1))
plot(full_post)

```

### Dimensional model

```{r}
ml.2 = glm(response_idx ~ gazeIDX*stimulus + version, data=PIT_conservative_tr, family = gaussian()) 
summary(ml.2)

# Plot fixed effects
plot_model(ml.2,type="pred", terms=c("stimulus","gazeIDX"),pred.type="fe", grid = FALSE)
plot_model(ml.2,type="pred", terms=c("gazeIDX","stimulus"),pred.type="fe", grid = FALSE)

# checking if excluding 253 makes a diff: eliminates the trend for stimulus, but no clear reason to exclude participant
#PIT_conservative_trX <- PIT_conservative_tr[-253,] 
#ml.2x = glm(response_idx ~ gazeIDX*stimulus + version, data=PIT_conservative_trX, family = gaussian()) 
#summary(ml.2x)
```

### Bayesian dimensional model
BayesFactor

```{r}
full <- lmBF(response_idx ~ gazeIDX + stimulus + gazeIDX:stimulus + version, data=PIT_conservative_ter, iterations = 10000)
describe_posterior(full, test=c("p_direction"))
interaction_null <- lmBF(response_idx ~ gazeIDX + stimulus + version, data=PIT_conservative_ter, iterations = 10000)
describe_posterior(interaction_null, test=c("p_direction"))
stgt_null <- lmBF(response_idx ~ stimulus + version, data=PIT_conservative_ter, iterations = 10000)
describe_posterior(stgt_null, test=c("p_direction"))
stimulus_null <- lmBF(response_idx ~ gazeIDX + version, data=PIT_conservative_ter, iterations = 10000)
describe_posterior(stimulus_null, test=c("p_direction"))

full/interaction_null
full/stgt_null
full/stimulus_null

# Diagnostics
full_post <- lmBF(response_idx ~ gazeIDX + stimulus + gazeIDX:stimulus + version, data=PIT_conservative_ter, iterations = 10000, posterior = TRUE)

#plots
par(mar=c(1,1,1,1))
plot(full_post)
```

# By hemiblock analyses: categorical ST/GT

```{r}
PIT_h_conservative_ter <- PIT_h_conservative_tr %>% 
  filter(!STGT=="IM")

PIT_h_conservative_ter$stimulus <- factor(PIT_h_conservative_ter$stimulus, levels = c("win", "nowin", "filler"))
PIT_h_conservative_ter$version <- as.factor(PIT_h_conservative_ter$version)
  
ml.4 = glm(response_idxh1 ~ STGT*stimulus + version, data=PIT_h_conservative_ter, family = gaussian()) 
summary(ml.4)
# Plot fixed effects
plot_model(ml.4,type="pred", terms=c("stimulus","STGT"),pred.type="fe", grid = FALSE, colors=c( "orangered","black"))

ml.5 = glm(response_idxh2 ~ STGT*stimulus + version, data=PIT_h_conservative_ter, family = gaussian()) 
summary(ml.5)

# Plot fixed effects
plot_model(ml.5,type="pred", terms=c("stimulus","STGT"),pred.type="fe", grid = FALSE, colors=c( "orangered","black"))

# checking if excluding 184 makes a diff: it doesn't
#PIT_h_conservative_terX <- PIT_h_conservative_ter[-184,] 
#ml.5x = glm(response_idxh2 ~ STGT*stimulus + version, data=PIT_h_conservative_terX, family = gaussian()) 
#summary(ml.5x)
```

# By hemiblock (hemiblock 1) analyses Bayesian: categorical ST/GT

```{r}
full <- lmBF(response_idxh1 ~ STGT + stimulus + STGT:stimulus + version, data=PIT_h_conservative_ter, iterations = 10000)
describe_posterior(full, test=c("p_direction"))
interaction_null <- lmBF(response_idxh1 ~ STGT + stimulus + version, data=PIT_h_conservative_ter, iterations = 10000)
describe_posterior(interaction_null, test=c("p_direction"))
stgt_null <- lmBF(response_idxh1 ~ stimulus + version, data=PIT_h_conservative_ter, iterations = 10000)
describe_posterior(stgt_null, test=c("p_direction"))
stimulus_null <- lmBF(response_idxh1 ~ STGT + version, data=PIT_h_conservative_ter, iterations = 10000)
describe_posterior(stimulus_null, test=c("p_direction"))

full/interaction_null
full/stgt_null
full/stimulus_null

# Diagnostics
full_post <- lmBF(response_idxh1 ~ STGT + stimulus + STGT:stimulus + version, data=PIT_h_conservative_ter, iterations = 10000, posterior = TRUE)

#plots
par(mar=c(1,1,1,1))
plot(full_post)
```

# By hemiblock (hemiblock 2) analyses Bayesian: categorical ST/GT

```{r}
full <- lmBF(response_idxh2 ~ STGT + stimulus + STGT:stimulus + version, data=PIT_h_conservative_ter, iterations = 10000)
describe_posterior(full,test=c("p_direction"))
interaction_null <- lmBF(response_idxh2 ~ STGT + stimulus + version, data=PIT_h_conservative_ter, iterations = 10000)
describe_posterior(interaction_null, test=c("p_direction"))
stgt_null <- lmBF(response_idxh2 ~ stimulus + version, data=PIT_h_conservative_ter, iterations = 10000)
describe_posterior(stgt_null, test=c("p_direction"))
stimulus_null <- lmBF(response_idxh2 ~ STGT + version, data=PIT_h_conservative_ter, iterations = 10000)
describe_posterior(stimulus_null, test=c("p_direction"))

full/interaction_null
full/stgt_null
full/stimulus_null

# Diagnostics
full_post <- lmBF(response_idxh1 ~ STGT + stimulus + STGT:stimulus + version, data=PIT_h_conservative_ter, iterations = 10000, posterior = TRUE)

#plots
par(mar=c(1,1,1,1))
plot(full_post)

```

# By hemiblock analyses by phenotype (ST and GT separately)

```{r}
st <- PIT_h_conservative_ter %>% 
  filter(STGT=="ST")

gt <- PIT_h_conservative_ter %>% 
  filter(STGT=="GT")

ml.6st = lm(response_idxh2 ~ stimulus, data=st) 
summary(ml.6st)

ml.6gt = lm(response_idxh2 ~ stimulus, data=gt) 
summary(ml.6gt)

# checking if excluding 97 makes a diff: results in a trend win vs filler but no clear reason to exclude the participant
#gtX <- gt[-97,]
#ml.6gtx = lm(response_idxh2 ~ stimulus, data=gtX) 
#summary(ml.6gtx)
```
#Bayesian hemiblock analyses by phenotype (ST and GT separately)


```{r}
# ST
full <- lmBF(response_idxh2 ~ stimulus, data=st, iterations = 10000)
describe_posterior(full)
full

# Diagnostics
full_post <- lmBF(response_idxh2 ~ stimulus, data=st, iterations = 10000, posterior = TRUE)

#plots
par(mar=c(1,1,1,1))
plot(full_post)

# GT
full <- lmBF(response_idxh2 ~ stimulus, data=gt, iterations = 10000)
describe_posterior(full)
full

# Diagnostics
full_post <- lmBF(response_idxh2 ~ stimulus, data=gt, iterations = 10000, posterior = TRUE)

#plots
par(mar=c(1,1,1,1))
plot(full_post)

```


# By hemiblock analysis: dimensional model

```{r}
# Hemiblock 1
ml.7 = glm(response_idxh1 ~ gazeIDX*stimulus + version, data=PIT_h_conservative_tr, family = gaussian()) 
summary(ml.7)
# Plot fixed effects
plot_model(ml.7,type="pred", terms=c("stimulus","gazeIDX"),pred.type="fe", grid = FALSE)

# Hemiblock 2
ml.8 = glm(response_idxh2 ~ gazeIDX*stimulus + version, data=PIT_h_conservative_tr, family = gaussian()) 
summary(ml.8)

# Plot fixed effects
plot_model(ml.8,type="pred", terms=c("stimulus","gazeIDX"),pred.type="fe", grid = FALSE)


# checking if excluding 228, 227 makes a diff: it doesn't
#PIT_h_conservative_trXX <- PIT_h_conservative_tr[-228,]
#PIT_h_conservative_trXXX <- PIT_h_conservative_tr[-227,]

#ml.7x = glm(response_idxh2 ~ gazeIDX*stimulus, data=PIT_h_conservative_trXX, family = gaussian()) 
#summary(ml.7x) # makes the trends significant, but doesn't change the concludions, and no other reason to exclude this observation
#ml.7xx = glm(response_idxh2 ~ gazeIDX*stimulus, data=PIT_h_conservative_trXXX, family = gaussian()) 
#summary(ml.7xx)
```

# Bayesian by hemiblock analysis: dimensional model
Bayes factor

```{r}
# Hemiblock 1
full <- lmBF(response_idxh1 ~ gazeIDX + stimulus + gazeIDX*stimulus + version, data=PIT_h_conservative_tr, iterations = 10000)
describe_posterior(full)
interaction_null <- lmBF(response_idxh1 ~ gazeIDX + stimulus + version, data=PIT_h_conservative_tr, iterations = 10000)
stgt_null <- lmBF(response_idxh1 ~ stimulus + version, data=PIT_h_conservative_tr, iterations = 10000)
stimulus_null <- lmBF(response_idxh1 ~ gazeIDX + version, data=PIT_h_conservative_tr, iterations = 10000)

full/interaction_null
full/stgt_null
full/stimulus_null

# Diagnostics
full_post <- lmBF(response_idxh1 ~ gazeIDX + stimulus + gazeIDX*stimulus + version, data=PIT_h_conservative_tr, iterations = 10000, posterior=TRUE)

#plots
par(mar=c(1,1,1,1))
plot(full_post)


# Hemiblock 2
full <- lmBF(response_idxh2 ~ gazeIDX + stimulus + gazeIDX*stimulus + version, data=PIT_h_conservative_tr, iterations = 10000)
describe_posterior(full)
interaction_null <- lmBF(response_idxh2 ~ gazeIDX + stimulus + version, data=PIT_h_conservative_tr, iterations = 10000)
stgt_null <- lmBF(response_idxh2 ~ stimulus + version, data=PIT_h_conservative_tr, iterations = 10000)
stimulus_null <- lmBF(response_idxh2 ~ gazeIDX + version, data=PIT_h_conservative_tr, iterations = 10000)

full/interaction_null
full/stgt_null
full/stimulus_null

# Diagnostics
full_post <- lmBF(response_idxh2 ~ gazeIDX + stimulus + gazeIDX*stimulus + version, data=PIT_h_conservative_tr, iterations = 10000, posterior=TRUE)

#plots
par(mar=c(1,1,1,1))
plot(full_post)

```

#Regression diagnostics

```{r}
plot(ml.1) #check out 184
cutoff <- 4/(nrow(PIT_conservative_ter)/3-length(ml.1$coefficients))
plot(ml.1, which=4)

plot(ml.2) #check out 253
cutoff <- 4/(nrow(PIT_conservative_tr)/3-length(ml.2$coefficients))
plot(ml.2, which=4)

plot(ml.4) 
cutoff <- 4/(nrow(PIT_h_conservative_ter)/3-length(ml.4$coefficients))
plot(ml.4, which=4)

plot(ml.5) #check out 184
cutoff <- 4/(nrow(PIT_h_conservative_ter)/3-length(ml.5$coefficients))
plot(ml.5, which=4)

plot(ml.6st) 
cutoff <- 4/(nrow(st)/3-length(ml.6st$coefficients))
plot(ml.6st, which=4)

plot(ml.6gt) #check out 97
cutoff <- 4/(nrow(gt)/3-length(ml.6gt$coefficients))
plot(ml.6gt, which=4)

plot(ml.7) #check out 228, 227
cutoff <- 4/(nrow(PIT_h_conservative_tr)/3-length(ml.7$coefficients))
plot(ml.7, which=4)

plot(ml.8) #check out 228, 227
cutoff <- 4/(nrow(PIT_h_conservative_tr)/3-length(ml.7$coefficients))
plot(ml.8, which=4)

```

# Plot

```{r}
PIT_h_l_conservative_ter <- pivot_longer(PIT_h_conservative_ter, cols = c(response_idxh1,response_idxh2), names_to = "half", values_to = "response_idx")
PIT_h_l_conservative_ter$halfactor <- ifelse(PIT_h_l_conservative_ter$half=="response_idxh1","hemiblock 1", "hemiblock 2")
PIT_h_l_conservative_ter$stimulus <- factor(PIT_h_l_conservative_ter$stimulus, levels = c("filler", "nowin", "win"))

p <- PIT_h_l_conservative_ter %>% ggplot(aes(x=stimulus, y=response_idx, fill=STGT)) +
  geom_boxplot() +
  xlab("") +
  scale_x_discrete(labels=(c("N","CS-", "CS+")))+
  scale_fill_manual(values=c("orange","grey")) + 
  theme_bw() +theme(plot.background = element_blank(),panel.grid.major = element_blank(),panel.grid.minor = element_blank()) + 
  theme(axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5), 
        axis.text.x=element_text(angle=0, size=12, face="bold", vjust=0.5),
        axis.text.y=element_text(angle=0, size=12, vjust=0.5),
        legend.position = "right",
        axis.title=element_text(size=14)) + ylab("Response index") + 
  facet_grid(. ~ halfactor)+ theme(strip.text.x = element_text(size=12, face="bold"))
#ggsave(filename="PIT_JN.tiff", plot=p, width = 6, height = 4.5 )
p
```
