---
title: "Pavlovian to Instrumental Transfer, Study 2"
author: "Mariya Cherkasova"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---
PIT analysis: Study dataset
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Load packages, read in the data
```{r, packages, include=FALSE}

rm(list=ls()) #clear env
library(lme4)
library(lattice)
library(lmerTest)
library(emmeans)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(influence.ME)
library(gmodels)#CI
library(corrplot)
library(arm)
library(gridExtra)
library(sjPlot)
library(olsrr)
library(brms)
library(bayestestR)
library(BayesFactor)
library(report)

```
### PIT1 data
Congruent response -left; incongruent response - right; CS+=win_fractal=blue (no re-labeling)
PIT=(number of congruent-incongruent choices/total number of choices)
```{r,include=FALSE}
# pit1data <- data.frame(id=0, half=0, trial=0, stimulus=0,fractal=0, click_l=0, click_r=0, click_out=0)
# 
# datadir <- "ST_NCRG_PIT/PIT1/results/"
# files <- list.files(path=datadir, pattern="*.*")
# for(i in files){
#   data <- read.delim(paste0(datadir,i,"/RESULTS_FILE.txt"))
#   id <- rep(i,nrow(data))
#   data <- cbind(id,data)
#   names(data)=names(pit1data)
#   pit1data=rbind(pit1data,data)
# }
# pit1data=pit1data[-1,]
# 
# pit1data$block <- ifelse(pit1data$trial<=5,1,ifelse(pit1data$trial<=9,2,3)) #block
# 
# # not considering task half
# pit1 <- pit1data %>% 
#   group_by(id,stimulus) %>% 
#   summarise(congruent=sum(click_l),incongruent=sum(click_r))  
# 
# pit1$response_idx <- (pit1$congruent-pit1$incongruent)/(pit1$congruent+pit1$incongruent)
# pit1$version <- rep(1,nrow(pit1))
# 
# # considering task half
# pit1_h <- pit1data %>% 
#   group_by(id,stimulus,half) %>% 
#   summarise(congruent=sum(click_l),incongruent=sum(click_r))  
# 
# pit1_h$response_idx <- (pit1_h$congruent-pit1_h$incongruent)/(pit1_h$congruent+pit1_h$incongruent)
# pit1_h$response_idx <- replace_na(pit1_h$response_idx,0) # Replace NAs
# pit1_h$version <- rep(1,nrow(pit1_h))

```
### PIT2
Congruent response -right; incongruent response - left; CS+=win_fractal=blue (no re-labeling)
```{r,include=FALSE}
# pit2data <- data.frame(id=0, half=0, trial=0, stimulus=0,fractal=0, click_l=0, click_r=0, click_out=0)
# 
# datadir <- "ST_NCRG_PIT//PIT2/results/"
# files <- list.files(path=datadir, pattern="*.*")
# for(i in files){
#   data <- read.delim(paste0(datadir,i,"/RESULTS_FILE.txt"))
#   id <- rep(i,nrow(data))
#   data <- cbind(id,data)
#   names(data)=names(pit2data)
#   pit2data=rbind(pit2data,data)
# }
# pit2data=pit2data[-1,]
# pit2data$block <- ifelse(pit2data$trial<=5,1,ifelse(pit1data$trial<=9,2,3)) #block
# 
# # not considering task half
# pit2 <- pit2data %>% 
#   group_by(id,stimulus) %>% 
#   summarise(congruent=sum(click_r),incongruent=sum(click_l)) #%>% 
# 
# pit2$response_idx <- (pit2$congruent-pit2$incongruent)/(pit2$congruent+pit2$incongruent)
# pit2$version <- rep(2,nrow(pit2))
# 
# # considering task half
# pit2_h <- pit2data %>% 
#   group_by(id,stimulus,half) %>% 
#   summarise(congruent=sum(click_r),incongruent=sum(click_l))  
# 
# pit2_h$response_idx <- (pit2_h$congruent-pit2_h$incongruent)/(pit2_h$congruent+pit2_h$incongruent)
# pit2_h$response_idx <- replace_na(pit2_h$response_idx,0) # Replace NAs
# pit2_h$version <- rep(2,nrow(pit2_h))

```
### PIT3
Congruent response -left; incongruent response -right; CS+=nowin_fractal=blue; in the data "stimulus" is already relabeled relative to the "fractal" so no relabeling necessary 
```{r,include=FALSE}
# pit3data <- data.frame(id=0, half=0, trial=0, stimulus=0,fractal=0, click_l=0, click_r=0, click_out=0)
# 
# datadir <- "ST_NCRG_PIT/PIT3/results/"
# files <- list.files(path=datadir, pattern="*.*")
# for(i in files){
#   data <- read.delim(paste0(datadir,i,"/RESULTS_FILE.txt"))
#   id <- rep(i,nrow(data))
#   data <- cbind(id,data)
#   names(data)=names(pit3data)
#   pit3data=rbind(pit3data,data)
# }
# pit3data=pit3data[-1,]
# pit3data$block <- ifelse(pit3data$trial<=5,1,ifelse(pit3data$trial<=9,2,3)) #block
# 
# # not considering task half
# pit3 <- pit3data %>% 
#   group_by(id,stimulus) %>% 
#   summarise(congruent=sum(click_l),incongruent=sum(click_r))  
# 
# pit3$response_idx <- (pit3$congruent-pit3$incongruent)/(pit3$congruent+pit3$incongruent)
# pit3$version <- rep(3,nrow(pit3))
# 
# # considering task half
# pit3_h <- pit3data %>% 
#   group_by(id,stimulus,half) %>% 
#   summarise(congruent=sum(click_l),incongruent=sum(click_r)) 
# 
# pit3_h$response_idx <- (pit3_h$congruent-pit3_h$incongruent)/(pit3_h$congruent+pit3_h$incongruent)
# pit3_h$response_idx <- replace_na(pit3_h$response_idx,0) # Replace NAs
# pit3_h$version <- rep(3,nrow(pit3_h))

```
### PIT4
Congruent response -right; incongruent response - left; CS+=nowin_fractal=blue; in the data "stimulus" is already relabeled relative to the "fractal" so no relabeling necessary 
```{r, include=FALSE}
# pit4data <- data.frame(id=0, half=0, trial=0, stimulus=0,fractal=0, click_l=0, click_r=0, click_out=0)
# 
# datadir <- "ST_NCRG_PIT/PIT4/results/"
# files <- list.files(path=datadir, pattern="*.*")
# for(i in files){
#   data <- read.delim(paste0(datadir,i,"/RESULTS_FILE.txt"))
#   id <- rep(i,nrow(data))
#   data <- cbind(id,data)
#   names(data)=names(pit4data)
#   pit4data=rbind(pit4data,data)
# }
# pit4data=pit4data[-1,]
# pit4data$block <- ifelse(pit4data$trial<=5,1,ifelse(pit4data$trial<=9,2,3)) #block
# 
# # not considering task half
# pit4 <- pit4data %>% 
#   group_by(id,stimulus) %>% 
#   summarise(congruent=sum(click_r),incongruent=sum(click_l)) #%>% 
# 
# pit4$response_idx <- (pit4$congruent-pit4$incongruent)/(pit4$congruent+pit4$incongruent)
# pit4$version <- rep(4,nrow(pit4))
# 
# # considering task half
# pit4_h <- pit4data %>% 
#   group_by(id,stimulus,half) %>% 
#   summarise(congruent=sum(click_r),incongruent=sum(click_l)) #%>% 
# 
# pit4_h$response_idx <- (pit4_h$congruent-pit4_h$incongruent)/(pit4_h$congruent+pit4_h$incongruent)
# pit4_h$response_idx <- replace_na(pit4_h$response_idx,0) # Replace NAs
# pit4_h$version <- rep(4,nrow(pit4_h))
# 
# PIT <- rbind(pit1,pit2,pit3,pit4)
# write.csv(PIT, file="pit_ncrg.csv",row.names=FALSE)
PIT <- read.csv("pit_ncrg.csv")

```
### Combine PIT with gaze index
```{r, include=FALSE}

PIT$stimulus <- factor(PIT$stimulus, levels = c("win", "nowin", "filler")) # CHANGE REFERENCE
PIT_h <- rbind(pit1_h,pit2_h,pit3_h,pit4_h)

stdata <- read.csv("STGT_CSplus2_tertiary_split_NCRG.csv")

# Compare ids in PIT and ST data and exclude
a <- stdata$id
b <- PIT$id
to_ex <- setdiff(b,a)

PIT_tr <- PIT %>% 
  filter(!id %in% to_ex) %>% 
  arrange(id,stimulus)
PIT_h_tr <- PIT_h %>% 
  filter(!id %in% to_ex) %>% 
  arrange(id,stimulus)

three <- 1:3
six <- 1:6
stexpandIDX_long <- expand.grid(six,stdata$gazeidx)
stexpandIDX_short <- expand.grid(three,stdata$gazeidx)
stgtxpand_short <- expand.grid(three,stdata$STGT_ter)
stgtxpand_long <- expand.grid(six,stdata$STGT_ter)

PIT_tr$gazeIDX <- stexpandIDX_short$Var2
PIT_tr$STGT <- stgtxpand_short$Var2
PIT_h_tr$gazeIDX <- stexpandIDX_long$Var2
PIT_h_tr$STGT <- stgtxpand_long$Var2

#view PIT response idx distribution
par(mfrow=c(1,2))
hist(PIT_tr$response_idx)
hist(PIT_h_tr$response_idx)
```

### Combine with IC data, trim data such that in only includes participants who performed the operant task above chance

```{r, include=FALSE}
ic <- read.csv("rating_IC_NCRG.csv")
names(ic)[1]<-"id"

icid <- ic$id
pitid <- PIT_tr$id
toX <- setdiff(icid,pitid)

ic <- ic %>% 
  filter(!id %in% toX)

three <- 1:3 #because there are three stimuli 
xpand_ic <- expand.grid(three,ic$IC)
xpand_ic_long <- expand.grid(six,ic$IC)

PIT_tr$ic <- xpand_ic$Var2
PIT_h_tr$ic <- xpand_ic_long$Var2

PIT_trtr <- PIT_tr %>% 
  filter(ic>53.9) 
PIT_h_trtr <- PIT_h_tr %>% 
  filter(ic>53.9) 

PIT_ter <- PIT_trtr %>% 
  filter(!STGT=="IM") 
PIT_h_ter <- PIT_h_trtr %>% 
  filter(!STGT=="IM") 
```

## ST/GT PIT models
Model not considering hemiblock
Excluding participants not looking at the CS or US, tertiary split
```{r}
ml = lm(response_idx ~ STGT*stimulus + version, data=PIT_ter) 
summary(ml)

# Plot 
plot_model(ml,type="pred", terms=c("stimulus", "STGT"),pred.type="fe", grid = FALSE, colors=c("black", "orangered"))
#plot_model(ml,type="pred", terms=c("stimulus"),pred.type="fe", grid = FALSE)

# checking if excluding 39 makes a diff: it doesn't
#PIT_terX <- PIT_ter[-39,] 
#mlx = lm(response_idx ~ STGT*stimulus + version, data=PIT_terX) 
#summary(mlx)
```

### ST/GT PIT models (Bayesian)
Model not considering hemiblock

```{r}
full <- lmBF(response_idx ~ STGT + stimulus + STGT:stimulus + version, data=PIT_ter, iterations = 10000)
describe_posterior(full, test=c("p_direction"))
interaction_null <- lmBF(response_idx ~ STGT + stimulus + version, data=PIT_ter, iterations = 10000)
stgt_null <- lmBF(response_idx ~ stimulus + version, data=PIT_ter, iterations = 10000)
stimulus_null <- lmBF(response_idx ~ STGT + version, data=PIT_ter, iterations = 10000)

full/interaction_null
full/stgt_null
full/stimulus_null


# Diagnostics
full_post <- lmBF(response_idx ~ STGT + stimulus + STGT:stimulus + version, data=PIT_ter, iterations = 10000, posterior = TRUE)

#plots
par(mar=c(1,1,1,1))
plot(full_post)

```

### ST/GT PIT models: by hemiblock, categorical (ST/GT)

```{r}
h1 <- PIT_h_ter %>% 
  filter(half==1)

h2 <- PIT_h_ter %>% 
  filter(half==2)

h1$stimulus <- factor(h1$stimulus, levels = c("win", "nowin", "filler")) 
h2$stimulus <- factor(h2$stimulus, levels = c("win", "nowin", "filler")) 

ml.3 = glm(response_idx ~ STGT*stimulus + version, data=h1, family = gaussian()) 
summary(ml.3)
# Plot fixed effects
plot_model(ml.3,type="pred", terms=c("stimulus","STGT"),pred.type="fe", grid = FALSE, colors=c("black","orangered"))

ml.4 = glm(response_idx ~ STGT*stimulus + version, data=h2, family = gaussian()) 
summary(ml.4)
# Plot fixed effects
plot_model(ml.4,type="pred", terms=c("stimulus","STGT"),pred.type="fe", grid = FALSE, colors=c("black","orangered"))

# checking if excluding 35 makes a diff: it doesn't
#h2X <- h2[-35,]
#ml.4x = glm(response_idx ~ STGT*stimulus + version, data=h2X, family = gaussian()) 
#summary(ml.4x)
```

### ST/GT PIT models: by hemiblock, categorical (ST/GT), Bayesian
Hemiblock 1
```{r}
full <- lmBF(response_idx ~ STGT + stimulus + STGT:stimulus + version, data=h1, iterations = 10000)
describe_posterior(full, test=c("p_direction"))
interaction_null <- lmBF(response_idx ~ STGT + stimulus + version, data=h1, iterations = 10000)
stgt_null <- lmBF(response_idx ~ stimulus + version, data=h1, iterations = 10000)
stimulus_null <- lmBF(response_idx ~ STGT + version, data=h1, iterations = 10000)

full/interaction_null
full/stgt_null
full/stimulus_null

# Diagnostics
full_post <- lmBF(response_idx ~ STGT + stimulus + STGT:stimulus + version, data=h1, iterations = 10000, posterior = TRUE)

#plots
par(mar=c(1,1,1,1))
plot(full_post)
```

Hemiblock 2
```{r}
full <- lmBF(response_idx ~ STGT + stimulus + STGT:stimulus + version, data=h2, iterations = 10000)
describe_posterior(full,test=c("p_direction"))
interaction_null <- lmBF(response_idx ~ STGT + stimulus + version, data=h2, iterations = 10000)
stgt_null <- lmBF(response_idx ~ stimulus + version, data=h2, iterations = 10000)
stimulus_null <- lmBF(response_idx ~ STGT + version, data=h2, iterations = 10000)

full/interaction_null
full/stgt_null
full/stimulus_null

# Diagnostics
full_post <- lmBF(response_idx ~ STGT + stimulus + STGT:stimulus + version, data=h2, iterations = 10000, posterior = TRUE)

#plots
par(mar=c(1,1,1,1))
plot(full_post)

```

### PIT Dimensional model

```{r}
ml.5 = glm(response_idx~ gazeIDX*stimulus + version, data=PIT_h_ter, family = gaussian()) 
summary(ml.5)

plot_model(ml.5,type="pred", terms=c("stimulus","gazeIDX"),pred.type="fe", grid = FALSE)


# checking if excluding 113,23 makes a diff: it doesn't
#PIT_h_terXXX<-PIT_h_ter[-113,] 
#ml.5xxx = glm(response_idx~ gazeIDX*stimulus*half + version, data=PIT_h_terXXX, family = gaussian()) 
#summary(ml.5xxx)

#PIT_h_terXXXX<-PIT_h_ter[-23,]
#ml.5xxxx = glm(response_idx~ gazeIDX*stimulus*half + version, data=PIT_h_terXXXX, family = gaussian()) 
#summary(ml.5xxxx)
```
### PIT Bayesian dimensional model

```{r}
full <- lmBF(response_idx ~ gazeIDX + stimulus + gazeIDX:stimulus + version, data=PIT_h_ter, iterations = 10000)
describe_posterior(full,test=c("p_direction"))
interaction_null <- lmBF(response_idx ~ gazeIDX + stimulus + version, data=PIT_h_ter, iterations = 10000)
stgt_null <- lmBF(response_idx ~ stimulus + version, data=PIT_h_ter, iterations = 10000)
stimulus_null <- lmBF(response_idx ~ gazeIDX + version, data=PIT_h_ter, iterations = 10000)

full/interaction_null
full/stgt_null
full/stimulus_null

# Diagnostics
full_post <- lmBF(response_idx ~ gazeIDX + stimulus + gazeIDX:stimulus + version, data=PIT_h_ter, iterations = 10000, posterior = TRUE)

#plots
par(mar=c(1,1,1,1))
plot(full_post)

```

### PIT: by hemiblock, dimensional
```{r}
ml.6 = glm(response_idx ~ gazeIDX*stimulus + version, data=h1, family = gaussian()) 
summary(ml.6)
# Plot fixed effects
plot_model(ml.6,type="pred", terms=c("stimulus","gazeIDX"),pred.type="fe", grid = FALSE, colors=c("black","orangered"))

ml.6 = glm(response_idx ~ gazeIDX*stimulus + version, data=h2, family = gaussian()) 
summary(ml.6)
# Plot fixed effects
plot_model(ml.6,type="pred", terms=c("stimulus","gazeIDX"),pred.type="fe", grid = FALSE, colors=c("black","orangered"))
```
### PIT: by hemiblock, dimensional, Bayesian
Hemiblock 1
```{r}
full <- lmBF(response_idx ~ gazeIDX + stimulus + gazeIDX*stimulus + version, data=h1, iterations = 10000)
describe_posterior(full, test=c("p_direction"))
interaction_null <- lmBF(response_idx ~ gazeIDX + stimulus + version, data=h1, iterations = 10000)
stgt_null <- lmBF(response_idx ~ stimulus + version, data=h1, iterations = 10000)
stimulus_null <- lmBF(response_idx ~ gazeIDX + version, data=h1, iterations = 10000)

full/interaction_null
full/stgt_null
full/stimulus_null

# Diagnostics
full_post <- lmBF(response_idx ~ gazeIDX + stimulus + gazeIDX*stimulus + version, data=h1, iterations = 10000, posterior=TRUE)

#plots
par(mar=c(1,1,1,1))
plot(full_post)
```

Hemiblock 2
```{r}
full <- lmBF(response_idx ~ gazeIDX + stimulus + gazeIDX*stimulus + version, data=h2, iterations = 10000)
describe_posterior(full,test=c("p_direction"))
interaction_null <- lmBF(response_idx ~ gazeIDX + stimulus + version, data=h2, iterations = 10000)
stgt_null <- lmBF(response_idx ~ stimulus + version, data=h2, iterations = 10000)
stimulus_null <- lmBF(response_idx ~ gazeIDX + version, data=h2, iterations = 10000)

full/interaction_null
full/stgt_null
full/stimulus_null

# Diagnostics
full_post <- lmBF(response_idx ~ gazeIDX + stimulus + gazeIDX*stimulus + version, data=h2, iterations = 10000, posterior = TRUE)

#plots
par(mar=c(1,1,1,1))
plot(full_post)

```

### Regression diagnostics

```{r}
plot(ml) #check out 39
cutoff <- 4/((nrow(PIT_h_ter)/3-length(ml$coefficients)))
plot(ml, which=4)

plot(ml.3) #check out 66
cutoff <- 4/((nrow(PIT_h_ter)/3-length(ml.3$coefficients)))
plot(ml.3, which=4)

plot(ml.4) 
cutoff <- 4/((nrow(PIT_h_ter)/3-length(ml.4$coefficients)))
plot(ml.4, which=4)

plot(ml.5) # check out 35
cutoff <- 4/((nrow(PIT_h_ter)/3-length(ml.5$coefficients)))
plot(ml.5, which=4)

plot(ml.6) # check out 23 and 113
cutoff <- 4/((nrow(PIT_h_ter)/3-length(ml.6$coefficients)))
plot(ml.6, which=4)
```
### Plot

```{r}
PIT_h_ter$halfactor <- ifelse(PIT_h_ter$half==1,"hemiblock 1", "hemiblock 2")
PIT_h_ter$stimulus <- factor(PIT_h_ter$stimulus, levels = c("filler", "nowin", "win"))

p <- PIT_h_ter %>% ggplot(aes(x=stimulus, y=response_idx, fill=STGT)) +
  geom_boxplot() +
  #geom_jitter(aes(group=STGT, colour=STGT), width=0.2)+
  xlab("") +
  scale_x_discrete(labels=(c("N","CS-", "CS+")))+
  scale_fill_manual(values=c("grey","orange")) + 
  theme_bw() +theme(plot.background = element_blank(),panel.grid.major = element_blank(),panel.grid.minor = element_blank()) + 
  theme(axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5), 
        axis.text.x=element_text(angle=0, size=12, face="bold", vjust=0.5),
        axis.text.y=element_text(angle=0, size=12, vjust=0.5),
        legend.position = "right",
        axis.title=element_text(size=14)) + ylab("Response index") + 
  facet_grid(. ~ halfactor)+ theme(strip.text.x = element_text(size=12, face="bold"))
#ggsave(filename="PIT_NCRG.tiff", plot=p, width = 6, height = 4.5 )


p

```
