---
title: "Pupil conditioning, Study 2"
author: "Mariya Cherkasova"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Load packages, read in the data
```{r, packages, include=FALSE}

rm(list=ls()) #clear env
library(lme4)
library(lattice)
library(lmerTest)
library(emmeans)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(influence.ME)
library(gmodels)#CI
library(corrplot)
library(arm)
library(gridExtra)
library(sjPlot)
library(brms)
library(bayestestR)

```

### Read in and combine data

```{r}
auc_data <- data.frame(stgt=0, id=0, cs=0, hemiblock=0,trial=0, auc=0, auc_500lag=0)

datadir <- "C:/Users/mashu/Documents/MATLAB/Pupil/STGT_NCRG/"
files <- list.files(path=datadir, pattern="*.txt")
for(i in files){
  data <- read.delim(paste0(datadir,i), header = TRUE, sep = "", dec = ".")
  stgt <- rep(i,nrow(data))
  data <- cbind(substr(i, 8, 9),data)
  names(data)=names(auc_data)
  auc_data=rbind(auc_data,data)
}
auc_data=auc_data[-1,]

stdata <- read.csv("STGT_CSplus2_tertiary_split_NCRG.csv")
version <- read.csv("rating_IC_NCRG.csv")

names(version)[1]<-"id"

#Trim PIT
versionid<-version$id
stid <- stdata$id
aucid <- unique(auc_data$id)
to_x <- setdiff(versionid,stid)
version <- version %>%
  filter(!id %in% to_x)

# Combine
auc_data <- auc_data %>% 
  arrange(id,trial)

forty <- 1:40
st_xpand <- expand.grid(forty,stdata$gazeidx)
version_xpand <- expand.grid(forty,version$version)

auc_data$version <- version_xpand$Var2
auc_data$gazeidx <- st_xpand$Var2
auc_data$cs <- as.factor(auc_data$cs)
auc_data$hemiblock <- as.factor(auc_data$hemiblock)
auc_data$version <- as.factor(auc_data$version)
auc_data$tr_scaled <- scale(auc_data$trial)#scaling needed for analyses with trial
auc_data$auc_500lag_scaled <- scale(auc_data$auc_500lag) 
auc_data$auc_500lag_rescaled <- rescale(auc_data$auc_500lag)

# visual AUC distribution
par(mfrow=c(2,2))
hist(auc_data$auc)
hist(auc_data$auc_500lag)
hist(auc_data$auc_500lag_scaled)
hist(auc_data$auc_500lag_rescaled)

auc_stgt <- auc_data %>% 
  filter(!stgt=="im")
st <- auc_stgt %>% 
  filter(stgt=="st")
gt <- auc_stgt %>% 
  filter(stgt=="gt")

cs.plus <- auc_data %>% filter(cs=="1")
cs.minus <- auc_data %>% filter(cs==-1)


```

### Model: STGT x CS x Trial

```{r}
# data should be rescaled if using trial or the dimensional model
ml <- lmer(auc_500lag_scaled ~ stgt*cs*tr_scaled + version + (1+cs+tr_scaled|id), data=auc_stgt, REML = FALSE, lmerControl(optimizer = "bobyqa")) 
summary(ml)
#control = lmerControl(optimizer ="Nelder_Mead")

# Plot fixed and random effects
plot_model(ml,type="pred", terms=c("cs", "stgt", "tr_scaled"),pred.type="fe", grid = FALSE, colors=c("black","orangered"))
plot_model(ml,type="pred", terms=c("tr_scaled"),pred.type="fe", grid = FALSE)
plot_model(ml,type="pred", terms=c("tr_scaled","cs"),pred.type="fe", grid = FALSE)
plot_model(ml,type="pred", terms=c("stgt"),pred.type="fe", grid = FALSE)
plot_model(ml,type="pred", terms=c("cs"),pred.type="fe", grid = FALSE)

```
### Model: STGT x CS x Trial (Bayesian)
Set priors

```{r}
#get default prior
get_prior(auc_500lag_scaled ~ stgt*cs*tr_scaled + version + (1+cs+tr_scaled|id), data=auc_stgt) 

#set priors
#we want to use uninformative priors, similar to BayesFactor, we will use Cauchy distribution with location of 0 and scale of 0.5 for fixed effects and default BRMS student priors for random effects

## Cauchy
fullpriors = c(set_prior("cauchy(0,0.5)", class = "Intercept"),
              set_prior("cauchy(0,0.5)", class = "b", coef="cs1"),
              set_prior("cauchy(0,0.5)", class = "b", coef="cs1:stgtst"),
              set_prior("cauchy(0,0.5)", class = "b", coef="cs1:stgtst:tr_scaled"),
              set_prior("cauchy(0,0.5)", class = "b", coef="cs1:tr_scaled"),
              set_prior("cauchy(0,0.5)", class = "b", coef="stgtst"),
              set_prior("cauchy(0,0.5)", class = "b", coef="stgtst:tr_scaled"),
              set_prior("cauchy(0,0.5)", class = "b", coef="tr_scaled"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version2"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version3"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version4"))
fullpriors

nullpriors = c(set_prior("cauchy(0,0.5)", class = "Intercept"),
              set_prior("cauchy(0,0.5)", class = "b", coef="cs1"),
              set_prior("cauchy(0,0.5)", class = "b", coef="cs1:stgtst"),
              set_prior("cauchy(0,0.5)", class = "b", coef="stgtst"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version2"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version3"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version4"))
nullpriors

nullpriors_cs = c(set_prior("cauchy(0,0.5)", class = "Intercept"),
              set_prior("cauchy(0,0.5)", class = "b", coef="stgtst"),
              set_prior("cauchy(0,0.5)", class = "b", coef="stgtst:tr_scaled"),
              set_prior("cauchy(0,0.5)", class = "b", coef="tr_scaled"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version2"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version3"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version4"))
nullpriors_cs

nullpriors_interaction = c(set_prior("cauchy(0,0.5", class = "Intercept"),
              set_prior("cauchy(0,0.5)", class = "b", coef="cs1"),
              set_prior("cauchy(0,0.5)", class = "b", coef="cs1:stgtst"),
              set_prior("cauchy(0,0.5)", class = "b", coef="stgtst"),
              set_prior("cauchy(0,0.5)", class = "b", coef="stgtst:tr_scaled"),
              set_prior("cauchy(0,0.5)", class = "b", coef="tr_scaled"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version2"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version3"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version4"))
nullpriors_interaction

nullpriors_interaction2 = c(set_prior("cauchy(0,0.5)", class = "Intercept"),
              set_prior("cauchy(0,0.5)", class = "b", coef="cs1"),
              set_prior("cauchy(0,0.5)", class = "b", coef="stgtst"),
              set_prior("cauchy(0,0.5)", class = "b", coef="stgtst:tr_scaled"),
              set_prior("cauchy(0,0.5)", class = "b", coef="tr_scaled"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version2"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version3"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version4"))
nullpriors_interaction2

nullpriors_interaction2 = c(set_prior("cauchy(0,0.5)", class = "Intercept"),
              set_prior("cauchy(0,0.5)", class = "b", coef="cs1"),
              set_prior("cauchy(0,0.5)", class = "b", coef="cs1:tr_scaled"),
              set_prior("cauchy(0,0.5)", class = "b", coef="stgtst"),
              set_prior("cauchy(0,0.5)", class = "b", coef="stgtst:tr_scaled"),
              set_prior("cauchy(0,0.5)", class = "b", coef="tr_scaled"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version2"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version3"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version4"))
nullpriors_interaction2

nullpriors_stgt = c(set_prior("cauchy(0,0.5)", class = "Intercept"),
              set_prior("cauchy(0,0.5)", class = "b", coef="cs1"),
              set_prior("cauchy(0,0.5)", class = "b", coef="cs1:tr_scaled"),
              set_prior("cauchy(0,0.5)", class = "b", coef="tr_scaled"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version2"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version3"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version4"))
nullpriors_stgt

nullpriors_interaction3 = c(set_prior("cauchy(0,0.5)", class = "Intercept"),
              set_prior("cauchy(0,0.5)", class = "b", coef="cs1"),
              set_prior("cauchy(0,0.5)", class = "b", coef="cs1:stgtst"),
              set_prior("cauchy(0,0.5)", class = "b", coef="cs1:tr_scaled"),
              set_prior("cauchy(0,0.5)", class = "b", coef="stgtst"),
              set_prior("cauchy(0,0.5)", class = "b", coef="stgtst:tr_scaled"),
              set_prior("cauchy(0,0.5)", class = "b", coef="tr_scaled"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version2"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version3"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version4"))
nullpriors_interaction3

```

### STGT x CS x Trial (Bayesian)
BRMS full model

```{r}
full <- brm(auc_500lag_scaled ~ cs + stgt + tr_scaled + cs*stgt + stgt*tr_scaled + cs*tr_scaled + cs*stgt*tr_scaled + version + (1+cs+tr_scaled|id), data=auc_stgt,  family=gaussian(), prior=fullpriors, save_pars = save_pars(all = TRUE), sample_prior = TRUE, silent = TRUE,iter = 10000) 
describe_posterior(full, test=c("p_direction"))
plot(full)
```

BRMS null model without trial or interactions with trial

```{r}
null_tr <- brm(auc_500lag_scaled ~ cs + stgt + cs*stgt + version + (1+cs|id), data=auc_stgt,  family=gaussian(), prior=nullpriors, save_pars = save_pars(all = TRUE), sample_prior = TRUE, silent = TRUE, iter = 10000) 
bridge = bayes_factor(full, null_tr)
bridge
describe_posterior(null_tr, test=c("p_direction"))
```

BRMS null model without CS or interactions with CS
```{r}
null_cs <- brm(auc_500lag_scaled ~ stgt + tr_scaled + stgt*tr_scaled + version + (1+tr_scaled|id), data=auc_stgt,  family=gaussian(), prior=nullpriors_cs, save_pars = save_pars(all = TRUE), sample_prior = TRUE, silent = TRUE, iter = 10000) 
describe_posterior(null_cs, test=c("p_direction"))
bridge_cs = bayes_factor(full, null_cs)
bridge_cs
```

BRMS null model without cs*trial interactions
```{r}

null_trcs <- brm(auc_500lag_scaled ~ cs + stgt + tr_scaled + cs*stgt + tr_scaled*stgt+version + (1+cs+tr_scaled|id), data=auc_stgt, family=gaussian(), prior=nullpriors_interaction, save_pars = save_pars(all = TRUE), sample_prior = TRUE, silent = TRUE, iter = 10000) 
describe_posterior(null_trcs, test=c("p_direction"))
bridge_trcs = bayes_factor(full, null_trcs)
bridge_trcs

```

BRMS null model without stgt
```{r}
null_stgt <- brm(auc_500lag_scaled ~ cs + tr_scaled + cs*tr_scaled + version + (1+cs+tr_scaled|id), data=auc_stgt,  family=gaussian(), prior=nullpriors_stgt, save_pars = save_pars(all = TRUE), sample_prior = TRUE, silent = TRUE, iter = 10000) 
describe_posterior(null_stgt, test=c("p_direction"))
bridge_stgt = bayes_factor(full, null_stgt)
bridge_stgt
```
BRMS null model without stgt x CS interaction

```{r}
null_stcs <- brm(auc_500lag_scaled ~ cs + stgt + tr_scaled + stgt*tr_scaled + cs*tr_scaled + version + (1+cs+tr_scaled|id), data=auc_stgt,  family=gaussian(), prior=nullpriors_interaction2, save_pars = save_pars(all = TRUE), sample_prior = TRUE, silent = TRUE, iter = 10000) 
describe_posterior(null_stcs, test=c("p_direction"))
bridge_stcs = bayes_factor(full, null_stcs)
bridge_stcs
```
BRMS null model without 3-way interaction

```{r}
null3w <- brm(auc_500lag_scaled ~ cs + stgt + tr_scaled + cs*stgt + stgt*tr_scaled + cs*tr_scaled + version + (1+cs+tr_scaled|id), data=auc_stgt,  family=gaussian(), prior=nullpriors_interaction3, save_pars = save_pars(all = TRUE), sample_prior = TRUE, silent = TRUE, iter = 10000) 
describe_posterior(null3w, test=c("p_direction"))
bridge_null3w = bayes_factor(full, null3w)
bridge_null3w
```

### Model: Gaze index x CS x trial

```{r}
# data should be rescaled if using trial for the dimensional model
ml.1 <- lmer(auc_500lag_scaled ~ gazeidx*cs*tr_scaled + version + (1+cs+tr_scaled|id), data=auc_data, REML = FALSE, lmerControl(optimizer = "bobyqa")) 
summary(ml.1)
#control = lmerControl(optimizer ="Nelder_Mead")

# Plot fixed and random effects
plot_model(ml.1,type="pred", terms=c("cs", "gazeidx", "tr_scaled"),pred.type="fe", grid = FALSE, colors=c("black","orangered"))
plot_model(ml.1,type="pred", terms=c("tr_scaled"),pred.type="fe", grid = FALSE)
plot_model(ml.1,type="pred", terms=c("cs","gazeidx"),pred.type="fe", grid = FALSE)
plot_model(ml.1,type="pred", terms=c("tr_scaled","cs"),pred.type="fe")
plot_model(ml.1,type="pred", terms=c("gazeidx"),pred.type="fe", grid = FALSE)

```

### Separate follow-up models: CS+ & CS-
CS+

```{r}

ml.csplus <- lmer(auc_500lag_scaled ~ gazeidx*tr_scaled + (1+tr_scaled|id), data=cs.plus, REML = FALSE, control = lmerControl(optimizer ="bobyqa")) 
summary(ml.csplus)

plot_model(ml.csplus,type="pred", terms=c("tr_scaled","gazeidx"),pred.type="fe", grid = FALSE)

```

CS-

```{r}
ml.minus <- lmer(auc_500lag_scaled ~ gazeidx*tr_scaled + (1+tr_scaled|id), data=cs.minus, REML = FALSE, control = lmerControl(optimizer ="bobyqa")) 
summary(ml.minus)

plot_model(ml.minus,type="pred", terms=c("tr_scaled","gazeidx"),pred.type="fe", grid = FALSE)
```

### Bayesian: gaze index x CS x Trial (Dimensional)
BRMS: set priors


```{r}
#examine densities
ggplot(auc_data, aes(x = auc_500lag_scaled, color = cs, fill = cs)) + geom_density(alpha = 0.2) +facet_wrap(~stgt)
ggplot(auc_data, aes(x = auc_500lag_scaled, color = cs, fill = cs)) + geom_density(alpha = 0.2) +facet_wrap(~tr_scaled)

#get default prior
get_prior(auc_500lag_scaled ~ cs*gazeidx*tr_scaled + version + (1+cs+tr_scaled|id), data=auc_data)

#set priors
#we want to use uninformative priors, similar to BayesFactor, we will use cauchy distribution with location of 0 and scale of 0.5 for fixed effects and default BRMS student priors for random effecs

## Cauchy
fullpriors = c(set_prior("cauchy(0,0.5)", class = "Intercept"),
              set_prior("cauchy(0,0.5)", class = "b", coef="cs1"),
              set_prior("cauchy(0,0.5)", class = "b", coef="cs1:gazeidx"),
              set_prior("cauchy(0,0.5)", class = "b", coef="cs1:gazeidx:tr_scaled"),
              set_prior("cauchy(0,0.5)", class = "b", coef="cs1:tr_scaled"),
              set_prior("cauchy(0,0.5)", class = "b", coef="gazeidx"),
              set_prior("cauchy(0,0.5)", class = "b", coef="gazeidx:tr_scaled"),
              set_prior("cauchy(0,0.5)", class = "b", coef="tr_scaled"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version2"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version3"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version4"))
fullpriors

nullpriors = c(set_prior("cauchy(0,0.5)", class = "Intercept"),
              set_prior("cauchy(0,0.5)", class = "b", coef="cs1"),
              set_prior("cauchy(0,0.5)", class = "b", coef="cs1:gazeidx"),
              set_prior("cauchy(0,0.5)", class = "b", coef="gazeidx"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version2"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version3"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version4"))
nullpriors


nullpriors_interaction = c(set_prior("cauchy(0,0.5", class = "Intercept"),
              set_prior("cauchy(0,0.5)", class = "b", coef="cs1"),
              set_prior("cauchy(0,0.5)", class = "b", coef="cs1:gazeidx"),
              set_prior("cauchy(0,0.5)", class = "b", coef="gazeidx"),
              set_prior("cauchy(0,0.5)", class = "b", coef="gazeidx:tr_scaled"),
              set_prior("cauchy(0,0.5)", class = "b", coef="tr_scaled"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version2"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version3"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version4"))
nullpriors_interaction

nullpriors_gazeidx = c(set_prior("cauchy(0,0.5)", class = "Intercept"),
              set_prior("cauchy(0,0.5)", class = "b", coef="cs1"),
              set_prior("cauchy(0,0.5)", class = "b", coef="cs1:tr_scaled"),
              set_prior("cauchy(0,0.5)", class = "b", coef="tr_scaled"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version2"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version3"),
              set_prior("cauchy(0,0.5)", class = "b", coef="version4"))
nullpriors_gazeidx
```

# Bayesian: gaze index x CS x Trial (Dimensional)
BRMS full model
```{r}
full <- brm(auc_500lag_scaled ~ cs + gazeidx + tr_scaled + cs*gazeidx + gazeidx*tr_scaled + cs*tr_scaled + cs*gazeidx*tr_scaled + version + (1+cs+tr_scaled|id), data=auc_data,  family=gaussian(), prior=fullpriors, save_pars = save_pars(all = TRUE), sample_prior = TRUE, silent = TRUE, iter = 10000) 
describe_posterior(full, test=c("p_direction"))
plot(full)

```

BRMS null model without trial or interactions with trial

```{r}
null_tr <- brm(auc_500lag_scaled ~ cs + gazeidx + cs*gazeidx + version + (1+cs|id), data=auc_data,  family=gaussian(), prior=nullpriors, save_pars = save_pars(all = TRUE), sample_prior = TRUE, silent = TRUE, iter = 10000) 
describe_posterior(null_tr, test=c("p_direction"))
bridge = bayes_factor(full, null_tr)
bridge
```

BRMS null model without cs x trail interactions

```{r}

null_cs_tr <- brm(auc_500lag_scaled ~ cs + gazeidx + tr_scaled + cs*gazeidx + gazeidx*tr_scaled + version + (1+cs+tr_scaled|id), data=auc_data,  family=gaussian(), prior=nullpriors_interaction, save_pars = save_pars(all = TRUE), sample_prior = TRUE, silent = TRUE, iter = 10000) 
describe_posterior(null_cs_tr, test=c("p_direction"))
bridge = bayes_factor(full, null_cs_tr)
bridge

```

BRMS null model without gaze index

```{r}
null_gazeidx <- brm(auc_500lag_scaled ~ cs + tr_scaled + cs*tr_scaled + version + (1+cs+tr_scaled|id), data=auc_data,  family=gaussian(), prior=nullpriors_gazeidx, save_pars = save_pars(all = TRUE), sample_prior = TRUE, iter = 10000) 
summary(null_gazeidx)
describe_posterior(null_gazeidx, test=c("p_direction"))
bridge_gazeidx = bayes_factor(full, null_gazeidx)
bridge_gazeidx
```

### Bayesian - Separate follow-up models: CS+ & CS-
BRMS set priors


```{r}
get_prior(auc_500lag_scaled ~ gazeidx*tr_scaled + (1+tr_scaled|id), data=cs.plus)

fullpriors.csplus = c(set_prior("cauchy(0,0.5)", class = "Intercept"),
              set_prior("cauchy(0,0.5)", class = "b", coef="gazeidx"),
              set_prior("cauchy(0,0.5)", class = "b", coef="gazeidx:tr_scaled"),
              set_prior("cauchy(0,0.5)", class = "b", coef="tr_scaled"))
fullpriors.csplus

nullpriors.csplus = c(set_prior("cauchy(0,0.5)", class = "Intercept"),
              set_prior("cauchy(0,0.5)", class = "b", coef="tr_scaled"))
nullpriors.csplus

```

Full model - cs plus
```{r}

full.csplus <- brm(auc_500lag_scaled ~ gazeidx*tr_scaled + (1+tr_scaled|id), data=cs.plus, family=gaussian(), prior=fullpriors.csplus, save_pars = save_pars(all = TRUE), sample_prior = TRUE, iter = 10000) 
summary(full.csplus)
describe_posterior(full.csplus, test=c("p_direction"))

```

Null model excluding gazeidx - cs plus
```{r}

null.csplus <- brm(auc_500lag_scaled ~ tr_scaled + (1+tr_scaled|id), data=cs.plus, family=gaussian(), prior=nullpriors.csplus, save_pars = save_pars(all = TRUE), sample_prior = TRUE, iter = 10000) 
summary(null.csplus)
describe_posterior(null.csplus, test=c("p_direction"))
bridge_null.csplus = bayes_factor(full, null.csplus)
bridge_null.csplus

```

Full model - cs minus

```{r}

full.csminus <- brm(auc_500lag_scaled ~ gazeidx*tr_scaled + (1+tr_scaled|id), data=cs.minus, family=gaussian(), prior=fullpriors.csplus, save_pars = save_pars(all = TRUE), sample_prior = TRUE, iter = 10000) 
summary(full.csminus)
describe_posterior(full.csminus, test=c("p_direction"))

```

Null model excluding gazeidx - cs minus
```{r}

null.csminus <- brm(auc_500lag_scaled ~ tr_scaled + (1+tr_scaled|id), data=cs.minus, family=gaussian(), prior=nullpriors.csplus, save_pars = save_pars(all = TRUE), sample_prior = TRUE, iter = 10000) 
summary(null.csminus)
describe_posterior(null.csminus, test=c("p_direction"))
bridge_null.minus = bayes_factor(full, null.csminus)
bridge_null.minus

```

### Regression diagnostics: ml

```{r}
# resid plot
plot(resid(ml))

#model_est <- influence(ml,"id") 
#saveRDS(model_est, file = "ppl_conditioningNCRG_influenceme_ml.rds")
model_est <- readRDS(file = "ppl_conditioningNCRG_influenceme_ml.rds")

model_est.dfB <- dfbetas(model_est)
plot(model_est,which="dfbetas",parameters=c(2,3,4,8,9),xlab="DFbetaS",ylab="Participant") # cutoff value 2/sqrt(n):0.33

cooks.distance(model_est,parameter=c(2,3,4,8,9))
plot(model_est,which ='cook' , sort=TRUE, xlab="Cook´s Distance", ylab="Participant") # cutoff value sqrt(4/n):0.33

sigtest(model_est, test=-1.96)$hemiblock2
sigtest(model_est, test=1.96)$`cs1:hemiblock2`

```

### Regression diagnostics: ml.1

```{r}
# resid plot
plot(resid(ml.1))

#model_est.1 <- influence(ml.1,"id") 
#saveRDS(model_est.1, file = "ppl_conditioningNCRG_influenceme_ml1.rds")
model_est.1 <- readRDS(file = "ppl_conditioningNCRG_influenceme_ml1.rds")

model_est.1.dfB <- dfbetas(model_est.1)
plot(model_est.1,which="dfbetas",parameters=c(2,3,4,8,9),xlab="DFbetaS",ylab="Participant") # cutoff value 2/sqrt(n): 0.33

cooks.distance(model_est.1,parameter=c(2,3,4,8,9))
plot(model_est.1,which ='cook' , sort=TRUE, xlab="Cook´s Distance", ylab="Participant") # cutoff value sqrt(4/n): 0.33

sigtest(model_est.1, test=-1.96)$tr_scaled
sigtest(model_est.1, test=1.96)$`cs1:tr_scaled`

```
