---
title: "VGT outcome phase fixations, Cherkasova et al, 2018"
author: "Mariya Cherkasova"
date: "`r Sys.Date()`"
output: html_document
---
Analysis of fixations during the outcome phase of the VGT (Cherkasova, 2018 dataset)
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Libraries

```{r,include=FALSE}
rm(list=ls()) #clear env
library(readr)
library(lme4)
library(lattice)
library(lmerTest)
library(emmeans)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(influence.ME)
library(gmodels)#CI
library(corrplot)
library(arm)
library(gridExtra)
library(sjPlot)
library(BayesFactor)
library(bayestestR)
```

Load data

```{r, include=FALSE}
STGT_tertiary_splitJN <- read_csv("STGT_CSplus2_tertiary_splitJN.csv")
fbFixC <- read_csv("JN_cued_group2_fix_feedback.csv")
fbFixUC <- read_csv("JN_uncued_group1_fix_feedback.csv")

# ptdt imports as chr, fix that
fbFixC$ptdt <- as.numeric(fbFixC$ptdt)
fbFixUC$ptdt <- as.numeric(fbFixUC$ptdt)

fbFixC$ptdt[is.na(fbFixC$ptdt)] <- 0
fbFixUC$ptdt[is.na(fbFixUC$ptdt)] <- 0
fbFixUC$id[is.na(fbFixUC$id)] <- 114
fbFixC$id[fbFixC$id==427] <- 127

```

Participant-wise % dwell time summaries for cued

```{r, include=FALSE}
fbFixC_summ <- fbFixC %>% 
  group_by(id,ia) %>% 
  summarise_each(funs(mean)) %>% 
  dplyr::select(!(trial)) %>% 
  pivot_wider(names_from = ia, values_from = c(dt,ptdt)) %>% 
  mutate(gazeidx_fb=ptdt_coins-ptdt_total)
fbFixC_summ$cues <- rep("cued",68)

histogram(fbFixC_summ$gazeidx_fb)
```

Participant-wise % dwell time summaries for uncued

```{r}
fbFixUC_summ <- fbFixUC %>% 
  group_by(id,ia) %>% 
  summarise_each(funs(mean)) %>% 
  dplyr::select(!(trial)) %>% 
  pivot_wider(names_from = ia, values_from = c(dt,ptdt)) %>% 
  mutate(gazeidx_fb=ptdt_coins-ptdt_total) 
fbFixUC_summ$cues <- rep("uncued",63)

histogram(fbFixUC_summ$gazeidx_fb)
```

Merge with STGT with feedback fixation data.

```{r}
fbFixC_summ$id <- as.character(fbFixC_summ$id)
STGT_tertiary_splitJN$id <- as.character(STGT_tertiary_splitJN$id)
fbFix <- rbind(fbFixUC_summ,fbFixC_summ)
fbFix_stgt <- inner_join(fbFix, STGT_tertiary_splitJN,by="id")

```

### Regressions & plots
Participants look at the feedback location more in the cued condition  but no interaction with gazeidx (phenotype)

```{r}
ml <- lm(gazeidx_fb~gazeidx*cues,data=fbFix_stgt)
summary(ml)

ml.1 <- lm(gazeidx_fb~STGT_ter*cues,data=filter(fbFix_stgt, !STGT_ter=="IM"))
summary(ml.1)


ggplot(fbFix_stgt, aes(x=gazeidx, y=gazeidx_fb,color=cues,fill=cues))+
       geom_point()+geom_smooth()

ggplot(fbFix_stgt, aes(x=STGT_ter, y=gazeidx_fb,color=cues,fill=cues))+
       geom_boxplot()
```

### Bayesian regression (dimensional)
Bayes Factor

```{r}
full <- lmBF(gazeidx_fb~gazeidx + cues + gazeidx:cues,data=fbFix_stgt, iterations = 10000)
describe_posterior(full,test=c("p_direction"))

null <- lmBF(gazeidx_fb~cues,data=fbFix_stgt,iterations = 10000)
describe_posterior(null,test=c("p_direction"))
full/null

full_post <- lmBF(gazeidx_fb~gazeidx + cues + gazeidx:cues,data=fbFix_stgt, iterations = 10000, posterior = TRUE)

#plots
par(mar=c(1,1,1,1))
plot(full_post)

```


### Bayesian regression (categorical)
Bayes Factor

```{r}
full <- lmBF(gazeidx_fb~STGT_ter + cues + STGT_ter:cues,data=filter(fbFix_stgt, !STGT_ter=="IM"), iterations = 10000)
describe_posterior(full,test=c("p_direction"))

null <- lmBF(gazeidx_fb~cues,data=filter(fbFix_stgt, !STGT_ter=="IM"),whichRandom="id",iterations = 10000)
describe_posterior(null,test=c("p_direction"))
full/null

full_post <- lmBF(gazeidx_fb~STGT_ter + cues + STGT_ter:cues,data=filter(fbFix_stgt, !STGT_ter=="IM"), iterations = 10000, posterior = TRUE)

#plots
par(mar=c(1,1,1,1))
plot(full_post)
```


### Regression diagnostics

```{r}

plot(ml)
plot(ml, which=4)

plot(ml.1)
plot(ml.1, which=4)

```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
